---
title: "SEFL10K6b_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Note that although trauma recall was first tested on and off cno twice \
there are carryover effects from prior inhibition in BLA group, seen as reduced freezing in second test.
In 10K6c, we therefore tested drug effects using between groups design.
```{r}

#load  files
data_vf = read.csv('SEFL10K6b_vfdata.csv',header=TRUE)
data_ld = read.csv('SEFL10K6b_lddata.csv',header=TRUE)
data_epm = read.csv('SEFL10K6b_epmdata.csv',header=TRUE)
data_of = read.csv('SEFL10K6b_ofdata.csv',header=TRUE)
groups = read.csv('SEFL10K6b_groups.csv',header=TRUE)


#factorize as necessary
groups$Animal = factor(groups$Animal)
data_vf$Animal = factor(data_vf$Animal)
data_ld$Animal = factor(data_ld$Animal)
data_of$Animal = factor(data_of$Animal)
data_epm$Animal = factor(data_epm$Animal)
data_ld$testnum = as.character(data_ld$testnum)
data_of$testnum = as.character(data_of$testnum)
data_epm$testnum = as.character(data_epm$testnum)


#get dataframe for drug order
drug_order = pivot_longer(
  data = groups[,c('Animal','Trec1','Trec2','Trec3','Trec4','Anx1_Drug','Anx2_Drug','Anx3_Drug','Anx4_Drug','Anx5_Drug','Anx6_Drug')],
  cols = c('Trec1','Trec2','Trec3','Trec4','Trec1','Trec2','Trec3','Trec4','Anx1_Drug','Anx2_Drug','Anx3_Drug','Anx4_Drug','Anx5_Drug','Anx6_Drug'),
  names_to = c('TestName'),
  values_to = 'Drug'
)
drug_order$testnum = as.numeric(gsub("\\D", "", drug_order$TestName))
drug_order$testtype = sapply(drug_order$TestName,function (x) {return(strsplit(x, "[[:digit:]]")[[1]][[1]])})

anxtest_order = pivot_longer(
  data = groups[,c('Animal','Anx1_Test','Anx2_Test','Anx3_Test','Anx4_Test','Anx5_Test','Anx6_Test')],
  cols = c('Anx1_Test','Anx2_Test','Anx3_Test','Anx4_Test','Anx5_Test','Anx6_Test'),
  names_to = c('TestName'),
  values_to = 'Test'
)
anxtest_order$testnum = as.numeric(gsub("\\D", "", anxtest_order$TestName))
anxtest_order$testtype = sapply(anxtest_order$TestName,function (x) {return(strsplit(x, "[[:digit:]]")[[1]][[1]])})

order_info = left_join(
  subset(drug_order, select=-c(TestName)),
  subset(anxtest_order, select=-c(TestName)), 
  by=c('Animal','testtype','testnum')
)
order_info$Test[order_info$testtype=='Trec'] = 'Trec'
order_info$Drug = factor(order_info$Drug, levels = c('veh','cno'))
order_info$testnum = as.character(order_info$testnum)


#add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")
data_ld = inner_join(x=groups,y=data_ld,by="Animal")
data_epm = inner_join(x=groups,y=data_epm,by="Animal")
data_of = inner_join(x=groups,y=data_of,by="Animal")

#add drug order 
data_vf = left_join(x=data_vf, y=order_info[order_info$Test=='Trec',], by=c('Animal'='Animal','subphase'='testnum'))
data_ld = left_join(x=data_ld, y=order_info[order_info$Test=='LD',], by=c('Animal'='Animal','testnum'='testnum'))
data_epm = left_join(x=data_epm, y=order_info[order_info$Test=='EPM',], by=c('Animal'='Animal','testnum'='testnum'))
data_of = left_join(x=data_of, y=order_info[order_info$Test=='OF',], by=c('Animal'='Animal','testnum'='testnum'))

```



# Drop subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]
data_epm = data_epm[data_epm$Exclude!=1,]
data_of = data_of[data_of$Exclude!=1,]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal, subphase, Region),
  .funs = list(motion=mean),
  .vars = c('motion')
)


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$component=='avg',]
traumatest$pair = 1
traumatest$pair[traumatest$subphase>2]=2

#Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Region, Drug, testnum),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))
ld.collapsed$test = 1
ld.collapsed$test[ld.collapsed$testnum>3] = 2


#Collapse epm data
data_epm = data_epm[data_epm$bin<5,]
data_epm$closed = data_epm$c1 + data_epm$c2
epm.collapsed = summarize_at(
  .tbl = group_by(data_epm, Animal, Region, Drug, testnum),
  .funs = list(mean),
  .vars = c('closed','Distance_in'))
epm.collapsed$test = 1
epm.collapsed$test[epm.collapsed$testnum>3] = 2

#Collapse of data
data_of = data_of[data_of$bin<5,]
of.collapsed = summarize_at(
  .tbl = group_by(data_of, Animal, Region, Drug, testnum),
  .funs = list(mean),
  .vars = c('DstFrmCnt_in','Distance_in'))
of.collapsed$test = 1
of.collapsed$test[of.collapsed$testnum>3] = 2

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component, Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Region, component, Drug, pair),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('dark','Distance_in'))


#epm stats
epm.stats = summarise_at(
  .tbl = group_by(
    .data = epm.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('closed','Distance_in'))


#of stats
of.stats = summarise_at(
  .tbl = group_by(
    .data = of.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('DstFrmCnt_in','Distance_in'))


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10k6b'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("red3", "royalblue3")
p.scale.fill = c("red3", "royalblue3")

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75
p.line.ind.size = .6
p.line.ind.alpha = .3

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3, 1.6, 3), "cm")
p.margin2 = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white", size=.75),
    strip.text = element_text(size=p.textsize.title-2, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    axis.line = element_line(color="black", size = p.line.axis.size),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.title.x = element_blank(),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```



## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Region,
      shape=Region,
      group=interaction(subphase,Region)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.9,.23),
    plot.margin = p.margin3
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



## Light dark
### Dark side
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Drug,
      y=dark_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
      data = ld.collapsed,
      aes(
        x = Drug,
        y = dark,
        group = Animal
      ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +

  labs(y = "% Time in Dark") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```


## Open field
### Center 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.OF.cnt = ggplot(
  data = of.stats,
  aes(x=Drug,
      y=DstFrmCnt_in_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 7
p.ymax = 9
p.yint = .5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.OF.cnt  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = DstFrmCnt_in_mean - DstFrmCnt_in_sem,
        ymax = DstFrmCnt_in_mean + DstFrmCnt_in_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = of.collapsed,
    aes(
      x = Drug,
      y = DstFrmCnt_in,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +

  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance From Center (in)") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "OF_Cnt.tiff", sep = '_'))}

```


## EPM

### Closed arms
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPM.cls = ggplot(
  data = epm.stats,
  aes(x=Drug,
      y=closed_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = .2
p.ymax = 1
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.EPM.cls  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = closed_mean - closed_sem,
        ymax = closed_mean + closed_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
      data = epm.collapsed,
      aes(
        x = Drug,
        y = closed,
        group = Animal
      ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(y = "% Time in Closed") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPM_Cls.tiff", sep = '_'))}

```





# Stats
### Sidak correction
```{r}

#Dunn-Sidak pcrit with 2 posthoc
comparisons = 2
pcrit_2 = 1 - (1 - .05)^(1/comparisons) 
#Dunn-Sidak pcrit with 4 posthoc
comparisons = 4
pcrit_4 = 1 - (1 - .05)^(1/comparisons)

```


### trauma
```{r}

trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```

### trauma recall
```{r}

traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  within = .(Drug),
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
traumatest.anova

```



### Light Dark Stats
#### Dark side time
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova

#vHC only
ld.dark.vhc.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='vHC',],
  dv = dark,
  wid = Animal,
  within = Drug,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.vhc.anova

#BLA only
ld.dark.bla.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='BLA',],
  dv = dark,
  wid = Animal,
  within = Drug,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.bla.anova

```

#### Distance travelled
```{r}

#comparison of time in dark side
ld.dist.anova = ezANOVA(
  data = ld.collapsed,
  dv = Distance_in,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
print(ld.dist.anova)


```


### EPM Stats
#### closed side time
```{r}

#comparison of time in closed arms
epm.closed.anova = ezANOVA(
  data = epm.collapsed,
  dv = closed,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.closed.anova

#veh only
epm.closed.veh.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Drug=='veh',],
  dv = closed,
  wid = Animal,
  #within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.closed.veh.anova


#bla only
epm.closed.bla.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Region=='BLA',],
  dv = closed,
  wid = Animal,
  within = Drug,
  #between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.closed.bla.anova

```

#### distance
```{r}

#comparison of distance travelled
epm.dist.anova = ezANOVA(
  data = epm.collapsed,
  dv = Distance_in,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.dist.anova


```


### OF Stats
#### Average distance from walls
```{r}

#comparison of time in closed arms
of.ctr.anova = ezANOVA(
  data = of.collapsed,
  dv = DstFrmCnt_in,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
of.ctr.anova

#vhc
of.ctr.vhc.anova = ezANOVA(
  data = of.collapsed[of.collapsed$Region=='vHC',],
  dv = DstFrmCnt_in,
  wid = Animal,
  within = Drug,
  #between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
of.ctr.vhc.anova

#bla
of.ctr.bla.anova = ezANOVA(
  data = of.collapsed[of.collapsed$Region=='BLA',],
  dv = DstFrmCnt_in,
  wid = Animal,
  within = Drug,
  #between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
of.ctr.bla.anova


```

#### distance
```{r}

#comparison of distance travelled
of.dist.anova = ezANOVA(
  data = of.collapsed,
  dv = Distance_in,
  wid = Animal,
  within = Drug,
  between = Region,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
of.dist.anova


```