---
title: "SEFL10K2_Analysis"
author: "Zach"
output:
  html_document:
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: readable
    toc: yes
    toc_depth: 6
  pdf_document:
    toc: yes
    toc_depth: '6'
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
```{r}

#load  files
data_vf = read.csv('SEFL10k2_vfdata.csv',header=TRUE)
data_ld = read.csv('SEFL10k2_lddata.csv',header=TRUE)
data_epm = read.csv('SEFL10k2_epmdata.csv',header=TRUE)
data_of = read.csv('SEFL10k2_ofdata.csv',header=TRUE)
groups = read.csv('SEFL10k2_groups.csv',header=TRUE)


##get dataframe for drug order
drug_order = pivot_longer(
  data = groups[,c('Animal','OF1','OF2','EPM1','EPM2','LD1','LD2','TR1','TR2')],
  cols = c('OF1','OF2','EPM1','EPM2','LD1','LD2','TR1','TR2'),
  names_to = 'TestName',
  values_to = 'Drug'
)
drug_order$Drug = recode(drug_order$Drug, 'Sal'='veh', 'uPSEM'='uPSEM')
drug_order$testnum = sapply(drug_order$TestName, function (x) {l = nchar(x); return(as.numeric(substr(x,l,l)))})
drug_order$test = sapply(drug_order$TestName,function (x) {l = nchar(x); return(substr(x,1,l-1))})


#factorize as necessary
groups$Animal = factor(groups$Animal)
data_vf$Animal = factor(data_vf$Animal)
data_ld$Animal = factor(data_ld$Animal)
data_epm$Animal = factor(data_epm$Animal)
data_of$Animal = factor(data_of$Animal)
drug_order$Animal = factor(drug_order$Animal)

 
#add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")
data_ld = inner_join(x=groups,y=data_ld,by="Animal")
data_of = inner_join(x=groups,y=data_of,by="Animal")
data_epm = inner_join(x=groups,y=data_epm,by="Animal")


#add drug order 
data_ld = left_join(x=data_ld, y=drug_order[drug_order$test=='LD',], by=c('Animal','testnum'))
data_of = left_join(x=data_of, y=drug_order[drug_order$test=='OF',], by=c('Animal','testnum'))
data_epm = left_join(x=data_epm, y=drug_order[drug_order$test=='EPM',], by=c('Animal','testnum'))

```


#Drop subjects
See `groups` dataframe for exclusion rationale.
```{r}
data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]
data_of = data_of[data_of$Exclude!=1,]
data_epm = data_epm[data_epm$Exclude!=1,]
```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma = data_vf[data_vf$phase=='trauma',]


#open field data collapsed
of.collapsed = summarize_at(
  .tbl = group_by(data_of, Animal, testnum, Drug, Region),
  .funs = list('mean'=mean,'sum'=sum),
  .vars = c('DstFrmCnt_in','Distance_in')
)


#epm data collapsed
data_epm$closed = data_epm$closed1 + data_epm$closed2
epm.collapsed = summarize_at(
  .tbl = group_by(data_epm, Animal, testnum, Drug, Region),
  .funs = list('mean'=mean,'sum'=sum),
  .vars = c('closed','Distance_in')
)


#ld data collapsed
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, testnum, Drug, Region),
  .funs = list('mean'=mean,'sum'=sum),
  .vars = c('dark','Distance_in')
)

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#of stats
of.stats = summarise_at(
  .tbl = group_by(
    .data = of.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('Distance_in_sum','DstFrmCnt_in_mean'))


#epm stats
epm.stats = summarise_at(
  .tbl = group_by(
    .data = epm.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('Distance_in_sum','closed_mean'))


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('Distance_in_sum','dark_mean'))


```


# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10k2'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("#26466D","red4",'paleturquoise4')
p.scale.fill = c("#26466D","red4",'paleturquoise4')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75
p.line.ind.size = .6
p.line.ind.alpha = .3

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3, .8, 3), "cm")
p.margin2 = plot.margin = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white", size=.75),
    strip.text = element_text(size=p.textsize.title-2, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    axis.line = element_line(color="black", size = p.line.axis.size),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.title.x = element_blank(),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Open field
### Distance 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.OF.dist = ggplot(
  data = of.stats,
  aes(x=Drug,
      y=Distance_in_sum_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1800
p.yint = 600
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.OF.dist  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_sum_mean - Distance_in_sum_sem,
        ymax = Distance_in_sum_mean + Distance_in_sum_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = of.collapsed,
    aes(
      x = Drug,
      y = Distance_in_sum,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance Travelled (in)") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "OF_Dist.tiff", sep = '_'))}

```

### Center 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.OF.cnt = ggplot(
  data = of.stats,
  aes(x=Drug,
      y=DstFrmCnt_in_mean_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 5
p.ymax = 9
p.yint = 1
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.OF.cnt  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = DstFrmCnt_in_mean_mean - DstFrmCnt_in_mean_sem,
        ymax = DstFrmCnt_in_mean_mean + DstFrmCnt_in_mean_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = of.collapsed,
    aes(
      x = Drug,
      y = DstFrmCnt_in_mean,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +

  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance From Center (in)") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "OF_Cnt.tiff", sep = '_'))}

```


## EPM
### Distance 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPM.dist = ggplot(
  data = epm.stats,
  aes(x=Drug,
      y=Distance_in_sum_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1200
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.EPM.dist  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_sum_mean - Distance_in_sum_sem,
        ymax = Distance_in_sum_mean + Distance_in_sum_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = epm.collapsed,
    aes(
      x = Drug,
      y = Distance_in_sum,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance Travelled (in)") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPM_Dist.tiff", sep = '_'))}

```

### Closed arms
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPM.cls = ggplot(
  data = epm.stats,
  aes(x=Drug,
      y=closed_mean_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = .2
p.ymax = 1
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.EPM.cls  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = closed_mean_mean - closed_mean_sem,
        ymax = closed_mean_mean + closed_mean_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
      data = epm.collapsed,
      aes(
        x = Drug,
        y = closed_mean,
        group = Animal
      ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(y = "% Time in Closed") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPM_Cls.tiff", sep = '_'))}

```



## Light dark
### Distance 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dist = ggplot(
  data = ld.stats,
  aes(x=Drug,
      y=Distance_in_sum_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1200
p.yint = 400
p.breaks = seq(p.ymin, p.ymax, p.yint)

#Create plot 
P.LD.dist  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_sum_mean - Distance_in_sum_sem,
        ymax = Distance_in_sum_mean + Distance_in_sum_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = ld.collapsed,
    aes(
      x = Drug,
      y = Distance_in_sum,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance Travelled (in)") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dist.tiff", sep = '_'))}

```

### Dark side
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Drug,
      y=dark_mean_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = .2
p.ymax = 1
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean_mean - dark_mean_sem,
        ymax = dark_mean_mean + dark_mean_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
      data = ld.collapsed,
      aes(
        x = Drug,
        y = dark_mean,
        group = Animal
      ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  facet_grid(cols = vars(Region)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +

  labs(y = "% Time in Dark") +
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```





# Statistics
## Open field
### Distance travelled
```{r}

of.dist.anova = ezANOVA(
  data = of.collapsed,
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE,
  detailed = TRUE
)
of.dist.anova


of.dist.vhc.anova = ezANOVA(
  data = of.collapsed[of.collapsed$Region=='vHC',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE,
  detailed = TRUE
)
of.dist.vhc.anova


of.dist.bla.anova = ezANOVA(
  data = of.collapsed[of.collapsed$Region=='BLA',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE,
  detailed = TRUE
)
of.dist.bla.anova


```

### Distance from center
```{r}

of.cnt.anova = ezANOVA(
  data = of.collapsed,
  dv = DstFrmCnt_in_sum,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE,
  detailed = TRUE
)
of.cnt.anova

```


## LightDark
### Distance travelled
```{r}

ld.dist.anova = ezANOVA(
  data = ld.collapsed,
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE
)
ld.dist.anova


ld.dist.vhc.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='vHC',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
ld.dist.vhc.anova


ld.dist.bla.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='BLA',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
ld.dist.bla.anova


```

### Dark side
```{r}

ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark_mean,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE
)
ld.dark.anova


ld.dark.vHC.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='vHC',],
  dv = dark_mean,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
ld.dark.vHC.anova


ld.dark.BLA.anova = ezANOVA(
  data = ld.collapsed[ld.collapsed$Region=='BLA',],
  dv = dark_mean,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
ld.dark.BLA.anova

```



## EPM
### Distance travelled
```{r}

epm.dist.anova = ezANOVA(
  data = epm.collapsed,
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE
)
epm.dist.anova

epm.dist.vhc.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Region=='vHC',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
epm.dist.vhc.anova

epm.dist.bla.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Region=='BLA',],
  dv = Distance_in_sum,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
epm.dist.bla.anova


```

### Closed arms
```{r}

epm.closed.anova = ezANOVA(
  data = epm.collapsed,
  dv = closed_mean,
  within = Drug,
  wid = Animal,
  between = Region,
  type = 3,
  white.adj = TRUE
)
epm.closed.anova

epm.closed.vHC.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Region=='vHC',],
  dv = closed_mean,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
epm.closed.vHC.anova

epm.closed.BLA.anova = ezANOVA(
  data = epm.collapsed[epm.collapsed$Region=='BLA',],
  dv = closed_mean,
  within = Drug,
  wid = Animal,
  type = 3,
  white.adj = TRUE
)
epm.closed.BLA.anova

```
