---
title: "SEFL10g2_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---



# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
Note that although some mice received 2 injections of anisomycin (3rd injection is saline), these animals are excluded here
```{r}

#load  files
data_vf = read.csv('SEFL10g2_vfdata.csv',header=TRUE)
data_ld = read.csv('SEFL10g2_lddata.csv',header=TRUE)
groups = read.csv('SEFL10g2_groups.csv',header=TRUE)


#factorize as necessary
groups$Animal = factor(groups$Animal)
groups = groups[groups$Group != 'T - ANI 2x',]
groups$Group = factor(groups$Group, levels=c('NT - Veh','T - Veh', 'T - ANI 3x'))
groups$Group = recode(groups$Group,'NT - Veh'= 'NT: veh', 'T - Veh' = 'T: veh','T - ANI 3x'='T: ani')
data_vf$Animal = factor(data_vf$Animal)
data_ld$Animal = factor(data_ld$Animal)


#add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")
data_ld = inner_join(x=groups,y=data_ld,by="Animal")

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Group),
  .funs = list(motion=mean),
  .vars = c('motion')
)
trauma.shockreact$subphase[trauma.shockreact$subphase=='baseline'] = 'bl'


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]


#Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Group),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))


```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma 
#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('dark','Distance_in'))


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10g2'

#ggsave
p.save = FALSE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 12
p.textsize.axis.text = 10

#Plot colors
p.scale.colour = c("white","darkgray","red","steelblue4",'darkgreen')
p.scale.fill = c("white","darkgray","red","steelblue4",'darkgreen')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .7
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .25

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", size = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin=unit(c(1,3.25,.1,3.25), "cm") #(top,right,bottom,left)
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Anisomycin effects
Here, impacts of systemically inject anisomycin after trauma are assessed.
#### Trauma
##### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 90
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  ggtitle("Trauma") + ylab("% Freezing") + xlab("Shock") +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin = margin(t=10)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.75,.2),
    plot.margin=unit(c(1, 3.2, .5, 3.2), "cm") #(top,right,bottom,left)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



##### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Shock = ggplot(
  data = trauma.shockreact.stats,
  aes(x=subphase,
      y=mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Trauma\nShock Reactivity") + ylab("Motion (au)") + xlab("") +
  
  p.basetheme +
  theme(
    axis.text.x= element_text(
      angle = 0,
      vjust=.5
    ),
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_ShockReact.tiff", sep = '_'))}


```



#### Light-Dark
##### Dark-Time
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    #fatten = p.width.error,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  ggtitle("Light-Dark") + ylab("% Time on Dark Side") + xlab("") +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```



##### Distance Travelled
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dist = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=Distance_in_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 160
p.yint = 40
p.breaks = seq(p.ymin,p.ymax,p.yint)
p.dot.binwidth = 2

#Create plot
P.LD.dist  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=Distance_in),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = .5,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_mean - Distance_in_sem,
        ymax = Distance_in_mean + Distance_in_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  ggtitle("Light-Dark:\nDistance Travelled") + ylab("Distance (in/min)") + xlab("") +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Distance.tiff", sep = '_'))}

```



#### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  ggtitle("Trauma Recall") + ylab("% Freezing") + xlab("") +
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```



#### Novel Stressor
##### Startle Response
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Startle = ggplot(
  data = novstressor.startle.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Startle  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','startle','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Novel Stressor\nStartle Response") + ylab("Motion (au)") + xlab("") +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Startle.tiff", sep = '_'))}

```



##### Pre/Post Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Prepost = ggplot(
  data = novstressor.prepost.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Prepost  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    aes(fill = Group),
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','post')) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Novel Stressor\nFreezing") + ylab("% Freezing") + xlab("") +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Freezing.tiff", sep = '_'))}

```



#### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Novel Stressor Recall") + ylab("% Freezing") + xlab("") +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest.tiff", sep = '_'))}

```



# Stats
## Anisomycin effects
#### Contrast sets
Here, contrasts for a-prior comparisons is set.
```{r}

#a-prior comparisons
comparisons = list(
  c('NT: veh', 'T: veh'),
  c('T: veh', 'T: ani'),
  c('NT: veh', 'T: ani')
)

pcrit = 1 - (1 - .05)^(1/length(comparisons)) #Dunn-Sidak pcrit

```

### Trauma Stats
```{r}
#comparison of trauma animals' freezing
trauma.fz.anova = ezANOVA(
  data = trauma.freezing[trauma.freezing$Group!='NT: veh',],
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Group,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```

#### SEFL Test Stats
```{r}

sefl.anova = ezANOVA(
  data = sefltest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE,
  detailed = TRUE
)
sefl.anova


sefltest.posthoc = list()
for (comp in comparisons){
  sefltest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    sefltest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
sefltest.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```



#### Trauma Test Stats
```{r}

traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova


traumatest.posthoc = list()
for (comp in comparisons){
  traumatest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    traumatest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
traumatest.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```



#### Light Dark Stats
###### Dark side time
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova


ld.dark.posthoc = list()
for (comp in comparisons){
  ld.dark.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      dark[Group==comp[1]], dark[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
ld.dark.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```



##### Distance travelled
```{r}

#comparison of time in dark side
ld.dist.anova = ezANOVA(
  data = ld.collapsed,
  dv = Distance_in,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dist.anova

ld.dist.posthoc = list()
for (comp in comparisons){
  ld.dist.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      Distance_in[Group==comp[1]], Distance_in[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
ld.dist.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```
