---
title: "SEFL10K6_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
Note that animals with control surgery in vHC/BLA combined in this analysis into common CTRL group.\
Note that although at the end of experiment trauma recall was done on and off cno, \
there are carryover effects from prior inhibition in BLA group, seen as reduced freezing \
in vehicle treated animals in first recall.
```{r}

#load  files
data_vf = read.csv('SEFL10K6_vfdata.csv',header=TRUE)
data_ld = read.csv('SEFL10K6_lddata.csv',header=TRUE)
data_epm = read.csv('SEFL10K6_epmdata.csv',header=TRUE)
groups = read.csv('SEFL10K6_groups.csv',header=TRUE)


#factorize as necessary
groups$Animal = factor(groups$Animal)
groups$Group = factor(groups$Group, levels=c('eGFP', 'BLA - HM4D', 'vHC - HM4D'))
groups$Group = recode_factor(groups$Group, 'eGFP' = 'eGFP: BLA/vHC', 'BLA - HM4D' = 'HM4D: BLA', 'vHC - HM4D' = 'HM4D: vHC')
data_vf$Animal = factor(data_vf$Animal)
data_ld$Animal = factor(data_ld$Animal)
data_epm$Animal = factor(data_epm$Animal)
data_epm$testnum = factor(data_epm$testnum)


#get dataframe for drug order
drug_order = pivot_longer(
  data = groups[,c('Animal','EPM1','EPM2','TR1','TR2')],
  cols = c('EPM1','EPM2','TR1','TR2'),
  names_to = 'TestName',
  values_to = 'Drug'
)
drug_order$testnum = sapply(drug_order$TestName, function (x) {l = nchar(x); return(as.numeric(substr(x,l,l)))})
drug_order$testnum = as.factor(drug_order$testnum)
drug_order$test = sapply(drug_order$TestName,function (x) {l = nchar(x); return(substr(x,1,l-1))})
drug_order$Drug = factor(drug_order$Drug, levels = c('veh','cno'))


#add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")
data_ld = inner_join(x=groups,y=data_ld,by="Animal")
data_epm = inner_join(x=groups,y=data_epm,by="Animal")


#add drug order 
data_epm = left_join(x=data_epm, y=drug_order[drug_order$test=='EPM',], by=c('Animal','testnum'))
data_vf = left_join(x=data_vf, y=drug_order[drug_order$test=='TR',], by=c('Animal'='Animal','subphase'='testnum'))

```



# Drop subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]
data_epm = data_epm[data_epm$Exclude!=1,]

```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Group),
  .funs = list(motion=mean),
  .vars = c('motion')
)


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]
sefltest_bymin = data_vf[data_vf$phase=='sefltest' & data_vf$subphase!='avg',]


#trauma recall with drug
traumatest_drug = data_vf[data_vf$phase=='traumatest_drug' & data_vf$component=='avg',]


#Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Group, Batch, Region),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))


#Collapse ld data
data_epm$closed = data_epm$closed1 + data_epm$closed2
data_epm = data_epm[data_epm$bin<5,]
epm.collapsed = summarize_at(
  .tbl = group_by(data_epm, Animal, Group, Batch, Region, Drug),
  .funs = list(mean),
  .vars = c('closed','Distance_in'))


# #subsetted dataframes to compare controls
ctrl.trauma = trauma.freezing[trauma.freezing$Group=='eGFP: BLA/vHC',]
ctrl.traumatest = traumatest[traumatest$Group=='eGFP: BLA/vHC',]
ctrl.ld = ld.collapsed[ld.collapsed$Group=='eGFP: BLA/vHC',]
ctrl.sefltest = sefltest[sefltest$Group=='eGFP: BLA/vHC',]

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('dark','Distance_in'))


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

sefltest_bymin.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest_bymin,
    component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#epm stats
epm.stats = summarise_at(
  .tbl = group_by(
    .data = epm.collapsed,
    Group, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('closed','Distance_in'))


#trauma recall with drug
traumatest_drug.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest_drug[traumatest_drug$subphase==1,],
    Group, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10k6'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75
p.line.ind.size = .6
p.line.ind.alpha = .2

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#Plot colors
p.scale.colour = c("white","red3", "royalblue3")
p.scale.fill = c("white","red3", "royalblue3")

#p.margin
p.margin1 = unit(c(1.2, 3.25, 0, 3.25), "cm")
p.margin2 = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.5, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.9,.2),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



#### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Shock = ggplot(
  data = trauma.shockreact.stats,
  aes(x=subphase,
      y=mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Trauma\nShock Reactivity",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x= element_text(
      angle = 0,
      vjust=.5,
      hjust=.5
    ),
    plot.margin = p.margin3,
    legend.position = c(.4,.85)
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_ShockReact.tiff", sep = '_'))}


```



### Light-Dark
#### Dark-Time
```{r, fig.width=4.5, fig.height=4.5}



#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```



#### Distance Travelled
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dist = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=Distance_in_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 160
p.yint = 40
p.breaks = seq(p.ymin,p.ymax,p.yint)
p.dot.binwidth = 2

#Create plot
P.LD.dist  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=Distance_in),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = .5,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_mean - Distance_in_sem,
        ymax = Distance_in_mean + Distance_in_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Light-Dark",
    x = "",
    y = "Distance (in/min)"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Distance.tiff", sep = '_'))}

```



### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Trauma",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```



### Novel Stressor
#### Startle Response
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Startle = ggplot(
  data = novstressor.startle.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Startle  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','startle','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.4,.85)
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Startle.tiff", sep = '_'))}

```



#### Pre/Post Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Prepost = ggplot(
  data = novstressor.prepost.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Prepost  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    aes(fill = Group),
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','post')) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.35,.85)
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Freezing.tiff", sep = '_'))}

```



### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 10
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest.tiff", sep = '_'))}

```



### EPM
#### Distance 
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPM.dist = ggplot(
  data = epm.stats,
  aes(x=Drug,
      y=Distance_in_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 300
p.yint = 100
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.EPM.dist  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_mean - Distance_in_sem,
        ymax = Distance_in_mean + Distance_in_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
    data = epm.collapsed,
    aes(
      x = Drug,
      y = Distance_in,
      group = Animal
    ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  facet_grid(cols = vars(Group)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
  
  labs(y = "Distance Travelled (in/min)") +
  p.basetheme 

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPM_Dist.tiff", sep = '_'))}

```

#### Closed arms
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPM.cls = ggplot(
  data = epm.stats,
  aes(x=Drug,
      y=closed_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.EPM.cls  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = closed_mean - closed_sem,
        ymax = closed_mean + closed_sem,),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_line(
      data = epm.collapsed,
      aes(
        x = Drug,
        y = closed,
        group = Animal
      ),
    alpha = p.line.ind.alpha,
    size = p.line.ind.size,
    color = 'black'
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  facet_grid(cols = vars(Group)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(y = "% Time in Closed") +
  p.basetheme +
  theme(
    strip.text = element_text(size=p.textsize.title-6, face="bold", hjust=.5),
    strip.background = element_rect(color=NA, fill=NA),
    plot.margin = unit(c(1.4, .8, 1.8, .8), "cm")
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPM_Cls.tiff", sep = '_'))}

```


### Plot comparison of vHC/BLA controls
##### Trauma
```{r}

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create base layer from group level data
P.ctrls.trauma = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.trauma,
      subphase,component,Region),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('freezing','motion')
  ),
  aes(
    x=component,
    y=freezing_mean,
    fill=Region,
    group = interaction(subphase,Region)
  )
) 

P.ctrls.trauma +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=c('white','darkgray')) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  ylab("% Freezing") + xlab("Shock") +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin = margin(t=10)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.8,.2),
    plot.margin = p.margin2
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_Trauma.tiff", sep = '_'))}
  

```

##### Light-Dark
```{r}


#Create base layer from group level data
P.ctrls.LD.dark = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.ld,
      Region),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('dark','Distance_in')
  ),
  aes(
    x=Region,
    y=dark_mean,
    fill=Region
  )
) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.ld,
    aes(x=Region,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=c('white','darkgray')) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +

  ggtitle("Light-Dark") + ylab("% Time on Dark Side") + xlab("") +
  
  p.basetheme

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_LD_Dark.tiff", sep = '_'))}


```



##### TraumaRecall
```{r}

#Create base layer from group level data
P.ctrls.traumatest = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.traumatest,
      Region),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('freezing','motion')
  ),
  aes(
    x=Region,
    y=freezing_mean,
    fill=Region
  )
) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.traumatest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.traumatest,
    aes(x=Region,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=c('white','darkgray')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Trauma Recall") + ylab("% Freezing") + xlab("") +
  
  p.basetheme

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_TraumaRecall.tiff", sep = '_'))}


```

##### SEFL Test
```{r}


#Create base layer from group level data
P.ctrls.sefltest = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.sefltest,
      Region),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('freezing','motion')
  ),
  aes(
    x=Region,
    y=freezing_mean,
    fill=Region
  )
) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 30
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.sefltest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.sefltest,
    aes(x=Region,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=c('white','darkgray')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  ggtitle("Novel Stressor") + ylab("% Freezing") + xlab("") +
  
  p.basetheme

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_SEFLTest.tiff", sep = '_'))}


```



# Stats
## Contrast sets
Here, contrasts for a-prior comparisons is set.
Currently, all planned comparisons performed independent of omnibus because of 
heteroscedasticity. Comparisons were performed using both Welch procedure and
hccm standard errors and rendered the same pattern of results.
```{r}

#a-prior comparisons
comparisons = list(
  c('eGFP: BLA/vHC', 'HM4D: BLA'),
  c('eGFP: BLA/vHC', 'HM4D: vHC')
)

pcrit = 1 - (1 - .05)^(1/length(comparisons)) #Dunn-Sidak pcrit

#function to perform hccm coefficient tests
coeftest.hccm = function(linmod) {
  tests = coeftest(linmod, hccm(linmod, 'hc3'))
  return(list('tests'=tests, 'df'=linmod$df.residual))
}

```

### Trauma
```{r}

trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Group,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```


### Light Dark Stats
#### Dark side time
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova

ld.dark.posthoc = list()
ld.dark.hccm.posthoc = list()
for (comp in comparisons){
  ld.dark.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      dark[Group==comp[1]], dark[Group==(comp)[2]],
      var.equal = FALSE
    ))
  linmod = lm(
    dark~Group, 
    data = ld.collapsed,
    subset = ld.collapsed$Group==comp[1] | ld.collapsed$Group==comp[2]
  )
  ld.dark.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
ld.dark.posthoc
#ld.dark.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```


#### Distance travelled
```{r}

#comparison of time in dark side
ld.dist.anova = ezANOVA(
  data = ld.collapsed,
  dv = Distance_in,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
print(ld.dist.anova)

ld.dist.posthoc = list()
ld.dist.hccm.posthoc = list()
for (comp in comparisons){
  ld.dist.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      Distance_in[Group==comp[1]], Distance_in[Group==(comp)[2]],
      var.equal = FALSE
    ))
  linmod = lm(
    Distance_in~Group, 
    data = ld.collapsed,
    subset = ld.collapsed$Group==comp[1] | ld.collapsed$Group==comp[2]
  )
  ld.dist.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
ld.dist.posthoc
#ld.dist.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```


### Trauma Test Stats
```{r}

traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova

```


### SEFL Test Stats
```{r}

sefl.anova = ezANOVA(
  data = sefltest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
sefl.anova


sefltest.posthoc = list()
sefltest.hccm.posthoc = list()
for (comp in comparisons){
  sefltest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    sefltest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
  linmod = lm(
    freezing~Group, 
    data = sefltest,
    subset = sefltest$Group==comp[1] | sefltest$Group==comp[2]
  )
  sefltest.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
sefltest.posthoc
#sefltest.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```





### EPM Stats
```{r}

#comparison of time in closed arms
epm.closed.anova = ezANOVA(
  data = epm.collapsed,
  dv = closed,
  wid = Animal,
  within = Drug,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.closed.anova

#comparison of distance travelled
epm.dist.anova = ezANOVA(
  data = epm.collapsed,
  dv = Distance_in,
  wid = Animal,
  within = Drug,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.dist.anova


epm.closed.posthoc = list()
epm.dist.posthoc = list()
for (group in levels(epm.collapsed$Group)){
  
  epm.closed.posthoc[[group]] = ezANOVA(
    data = epm.collapsed[epm.collapsed$Group==group,],
    wid = Animal,
    dv = closed,
    within = Drug,
    detailed = TRUE
  )
  
  epm.dist.posthoc[[group]] = ezANOVA(
    data = epm.collapsed[epm.collapsed$Group==group,],
    wid = Animal,
    dv = Distance_in,
    within = Drug,
    detailed = TRUE
  )

}

epm.closed.posthoc

```



### BLA/vHC Controls
#### Trauma
```{r}

ctrl.trauma.fz.anova = ezANOVA(
  data = ctrl.trauma,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
ctrl.trauma.fz.anova

```

#### Trauma Test
```{r}

ctrl.traumatest.fz.anova = ezANOVA(
  data = ctrl.traumatest,
  dv = freezing,
  wid = Animal,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
ctrl.traumatest.fz.anova

```

#### Light Dark
```{r}

ctrl.ld.anova = ezANOVA(
  data = ctrl.ld,
  dv = dark,
  wid = Animal,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
ctrl.ld.anova

```

#### SEFL Test
```{r}

ctrl.sefltest.fz.anova = ezANOVA(
  data = ctrl.sefltest,
  dv = freezing,
  wid = Animal,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
ctrl.sefltest.fz.anova

```
