---
title: "SEFL10K9_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Load  spike times.\
Note that drug was applied to bath after 10 minute baseline.
Recording proceeded for additional 50 minutes
```{r}

#load  files
spikes = read.csv('SEFL10K9_spiketimes.csv',header=TRUE)

```


# Bin spikes across time
Define number of spikes in evenly spaced bins across 60 minutes recording
```{r}

binsize = 600 #bin size, in seconds
nbins = 6 

spikes$spike_bin = factor(spikes$SpikeT_sec %/% binsize, levels = 0:(nbins-1))

spikes_binned = list()
for (c in unique(spikes$Cell)) {
  spikes_binned[[c]] = as.data.frame(
    table(spikes$spike_bin[spikes$Cell==c], dnn = 'bin')
    )
  bl = spikes_binned[[c]]$Freq[1]
  spikes_binned[[c]]$NrmFreq = (spikes_binned[[c]]$Freq/bl)*100
}

spikes_binned = bind_rows(spikes_binned, .id = "Cell")
spikes_binned = left_join(
  unique(spikes[,c('Cell','Region','HM4D')]), spikes_binned, 
  by='Cell'
)

```


# Define pre/post
Baseline before drug administration was 10 minutes.
Post used was final 10 minutes
```{r}

component = c('bl', 'void','void','void','void','post')
spikes_binned = left_join(spikes_binned, data.frame('bin'=as.factor(0:5), component), by='bin')

```


# Calculate pre/post activity and get summary stats
```{r}

#get pre/post for each cell
spike_summary = summarise_at(
  .tbl = group_by(
    .data = spikes_binned[spikes_binned$component!='void',],
    Cell, Region, HM4D, component),
  .funs = list(NrmFreq=~mean(.)),
  .vars = c('NrmFreq')
)

spike_summary$group = droplevels(with(spike_summary, interaction(Region, HM4D)))
spike_summary$group = recode_factor(
  spike_summary$group, 
  'vCA1.neg'='HM4D-',
  'BLA.pos'='HM4D+: BLA',
  'vCA1.pos'='HM4D+: vHC'
  )

#get mean summary for each pair.
spike_summary.stats = summarise_at(
  .tbl = group_by(
    .data = spike_summary,
    Region, group, component),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('NrmFreq')
)

```


# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10K9'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("white","red3", "royalblue3")
p.scale.fill = c("white","red3", "royalblue3")


#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3


#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```

## Firing Rate plot
```{r}

#Define plot specific parameters
p.ymin = 40
p.ymax = 110
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

p.spikefreq = ggplot(
  data = spike_summary.stats,
  aes(
    x = component,
    y = mean,
    group = group,
    fill = group
  )
)

p.spikefreq + 
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error
        )) +
  
  geom_line() +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('pre','post')) +
  
  labs(
    y = '% Baseline Firing'
  ) +
  
  p.basetheme +
  theme(
    axis.title.x = element_blank(),
    axis.text.x = element_text(angle=0, hjust=.5),
    legend.position = c(1.7,.2),
    plot.margin = margin(2.4,3.75,2.45,3.75, unit='cm')
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Firing.tiff", sep = '_'))}  

```




# Stats

```{r}

spike.anova = ezANOVA(
  data = spike_summary,
  dv = NrmFreq,
  wid = Cell,
  within = component,
  between = group,
  type = 3,
  detailed = TRUE
)
spike.anova

spike.hm4dneg.anova = ezANOVA(
  data = spike_summary[spike_summary$HM4D=='neg',],
  dv = NrmFreq,
  wid = Cell,
  within = component,
  type = 3,
  detailed = TRUE
)
spike.hm4dneg.anova

spike.hm4dpos.anova = ezANOVA(
  data = spike_summary[spike_summary$HM4D=='pos',],
  dv = NrmFreq,
  wid = Cell,
  within = component,
  between = group,
  type = 3,
  detailed = TRUE
)
spike.hm4dpos.anova

spike.hm4dbla.anova = ezANOVA(
  data = spike_summary[spike_summary$group=='HM4D+: BLA',],
  dv = NrmFreq,
  wid = Cell,
  within = component,
  type = 3,
  detailed = TRUE
)
spike.hm4dbla.anova

spike.hm4dvhc.anova = ezANOVA(
  data = spike_summary[spike_summary$group=='HM4D+: vHC',],
  dv = NrmFreq,
  wid = Cell,
  within = component,
  type = 3,
  detailed = TRUE
)
spike.hm4dvhc.anova

```
