---
title: "SEFL7c_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
Note that between trauma and trauma recall & novel stressor, animals underwent cocaine conditioned place preference. \
This entailed the receipt of 3 injections of cocaine (20 mg/kg, ip). No differences were observed in final preference (in fact, no pref observed)
```{r}

#load  files
data_vf = read.csv('SEFL7c_vfdata.csv',header=TRUE)
data_cpp = read.csv('SEFL7c_cppdata.csv',header=TRUE)
groups = read.csv('SEFL7c_groups.csv',header=TRUE)

#make animal factor
groups$Animal = factor(groups$Animal)
data_vf$Animal = factor(data_vf$Animal)
data_cpp$Animal = factor(data_cpp$Animal)

#add group info to data files
data_vf = right_join(x=groups,y=data_vf,by="Animal")
data_cpp = right_join(x=groups,y=data_cpp,by="Animal")

```



# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$component=='avg',]

#nov stressor data
novstressor.cs = data_vf[data_vf$phase=='mildstressor' & (data_vf$component=='bl' | data_vf$component=='cs'),]
novstressor.shock = data_vf[data_vf$phase=='mildstressor' & (data_vf$component=='bl' | data_vf$component=='shock'),]

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group, subphase),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novstressor training sessions
novstressor.cs.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.cs,
    component,subphase, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
novstressor.cs.stats$GroupInt = droplevels(
  interaction(novstressor.cs.stats$Group, novstressor.cs.stats$component, sep=": ")
  )

novstressor.shock.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.shock,
    component, subphase,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
novstressor.shock.stats$GroupInt = droplevels(
  interaction(novstressor.shock.stats$Group, novstressor.shock.stats$component, sep=": ")
  )

```

# CPP data
3 chamber cpp was used.
For tests, after being confined to center for 3 minutes,  animals were allowed to explore all 3 chambers for 10 minutes
For training, animals were confined to one of two outer chambers for 20 minutes, immed. after receiving 20 mg/kg cocaine, i.p.
Animals were given two pretests, followed by 4 training sessions (cocaine on either odd or even days).  
Following 3 post-training test sessions, a final drug-primed session was run
Training and test sessions were always separated by 1 day.

## subset cpp data
```{r}

# get overall session data and define drug side
data_cpp = data_cpp[data_cpp$bin=='all',]
data_cpp$drugside = data_cpp$left
data_cpp$drugside[data_cpp$coc_side=='right'] = data_cpp$right[data_cpp$coc_side=='right']

# define session order
data_cpp$subphase = factor(
  data_cpp$subphase,
  levels = c('Pretest1','Pretest2','Training1','Training2','Training3','Training4','ET_1','ET_2','ET_3','Priming Test')
)

# get cpp pretest/test and training data
data_cpp.test = data_cpp[data_cpp$phase!='Training',]
data_cpp.training = data_cpp[data_cpp$phase=='Training',]

#for training days define drug days for each animal
data_cpp.training$drug = 'sal'
data_cpp.training$drug[
  data_cpp.training$coc_trndays=='odd' &
    (data_cpp.training$subphase=='Training1'|data_cpp.training$subphase=='Training3')
] = 'coc'
data_cpp.training$drug[
  data_cpp.training$coc_trndays=='even' &
    (data_cpp.training$subphase=='Training2'|data_cpp.training$subphase=='Training4')
] = 'coc'
data_cpp.training$drug = factor(data_cpp.training$drug, levels=c('sal','coc'))

#define day bins
data_cpp.training$days = 'd1to2'
data_cpp.training$days[data_cpp.training$subphase=='Training3'|data_cpp.training$subphase=='Training4'] = 'd3to4'

```

## get summary stats
```{r}

#cpp training
cpp.training.stats = summarise_at(
  .tbl = group_by(
    .data = data_cpp.training,
    days, drug,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('Distance_in')
)

cpp.training.ANOVA = ezANOVA(
  data = data_cpp.training,
  wid = Animal,
  dv = Distance_in,
  within = .(drug, days),
  between = Group,
  white.adjust = TRUE,
  detailed = TRUE,
  type = 3
)
cpp.training.ANOVA

#cpp test
cpp.test.stats = summarise_at(
  .tbl = group_by(
    .data = data_cpp.test,
    subphase, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('drugside')
)

cpp.test.ANOVA = ezANOVA(
  data = data_cpp.training,
  wid = Animal,
  dv = Distance_in,
  within = .(subphase),
  between = Group,
  white.adjust = TRUE,
  detailed = TRUE,
  type = 3
)
cpp.test.ANOVA

```


# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '7c'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 18
p.textsize.legend =13
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("white","thistle4","#26466D","red4",'paleturquoise4')
p.scale.fill = c("white","thistle4","#26466D","red4",'paleturquoise4')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#legend 
p.legend.position = c(.22,.9)

#margins
p.margin1 = unit(c(2, 1.25, 2.45, 2.25), 'cm') 
p.margin2 = unit(c(2,3.7,2.45,3.7), "cm") 
p.margin3 =  unit(c(1.3, 3.5, 1.45, 3.5), 'cm')

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", size = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=12,t=0), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.title.x = element_text(margin=margin(t=-1)),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='plain',
      angle = 0,
      vjust=.5,
      margin = margin(b=10,t=5)
      ),
    legend.position = 'right',
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Trauma Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=subphase,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=Group))

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_x_continuous(breaks = c(1,2)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Trauma",
    x = "Recall",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    legend.position = c(.42,.95),
    legend.direction = 'horizontal',
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```


## Nov Stressor
### CS
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.NovSts.CS = ggplot(
  data = novstressor.cs.stats,
  aes(x=subphase,
      y=freezing_mean,
      fill=GroupInt,
      shape=GroupInt,
      group=GroupInt))

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.NovSts.CS  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=c('white','thistle4','white','thistle4')) +
  scale_shape_manual(values=c(24,24,21,21)) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_x_continuous(breaks = c(1:7)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Trauma",
    x = "Day",
    y = "% Freezing"
  ) +
  
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStsFZ.tiff", sep = '_'))}

```


### Shock
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.NovSts.shock = ggplot(
  data = novstressor.shock.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group))

#Define plot specific parameters
p.ymin = 0
p.ymax = 1000
p.yint = 200
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.NovSts.shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    shape = 21,
    size = p.point.size,
    stroke = p.point.stroke
  ) +
  
  facet_grid(cols = vars(subphase)) +
  
  scale_fill_manual(values=c('white','thistle4','white','thistle4')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    title = "Shock Reacitivty by Day",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=10,t=0), size=p.textsize.axis.title),
    axis.title.x = element_blank(),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = -90,
      hjust=0),
    legend.position = c(.2,.9),
    legend.direction = 'horizontal',
    plot.margin = unit(c(2, 1.25, 2.45, 1.25), 'cm')
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStsShock.tiff", sep = '_'))}

```

## Theoretical curves
Below, simulated examples of learning rate vs stimulus strength changes using Rescorla Wagner are plotted presented.
### Learning Rate
```{r}

trials = 7
l1 = 45
l2 = 45
a1 = .375
a2 = .9

learning.curves = data.frame(
  'trial' = seq(1,trials,1),
  'lambda1' = rep(l1, trials),
  'lambda2' = rep(l2, trials),
  'alpha1' = rep(a1, trials),
  'alpha2' = rep(a2, trials),
  'deltav1' = rep((l1-0)*a1, trials),
  'deltav2' = rep((l2-0)*a2, trials),
  'v1' = rep(0, trials),
  'v2' = rep(0, trials)
)

for (trial in 2:trials) {
  learning.curves[trial, 'v1'] = learning.curves[trial-1,'v1'] + learning.curves[trial-1,'deltav1']
  learning.curves[trial, 'v2'] = learning.curves[trial-1,'v2'] + learning.curves[trial-1,'deltav2']
  learning.curves[trial, 'deltav1'] = (l1 - learning.curves[trial,'v1']) * a1
  learning.curves[trial, 'deltav2'] = (l2 - learning.curves[trial,'v2']) * a2
}

learning.curves.v = pivot_longer(
  data = learning.curves[c('trial','lambda1','lambda2','alpha1','alpha2','v1','v2')],
  cols = c('v1','v2'),
  names_to = 'v'
)
learning.curves.v$v = factor(learning.curves.v$v)
learning.curves.v$v = recode(learning.curves.v$v, 'v1'='NT', 'v2'='T')


#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

p.learning.curves = ggplot(
  data = learning.curves.v,
  aes(x = trial, y = value, group = v, fill=v)
)

p.learning.curves + 
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = 21
  ) +
  
  scale_fill_manual(values=c('white','thistle4')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:trials) +
  
  ggtitle("Learning\nRate") + ylab("% Freezing") + xlab("Day") +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TheoreticalRate.tiff", sep = '_'))}


```


### Stim Strength
```{r}


trials = 7
l1 = 20
l2 = 45
a1 = .9
a2 = .9

learning.curves = data.frame(
  'trial' = seq(1,trials,1),
  'lambda1' = rep(l1, trials),
  'lambda2' = rep(l2, trials),
  'alpha1' = rep(a1, trials),
  'alpha2' = rep(a2, trials),
  'deltav1' = rep((l1-0)*a1, trials),
  'deltav2' = rep((l2-0)*a2, trials),
  'v1' = rep(0, trials),
  'v2' = rep(0, trials)
)

for (trial in 2:trials) {
  learning.curves[trial, 'v1'] = learning.curves[trial-1,'v1'] + learning.curves[trial-1,'deltav1']
  learning.curves[trial, 'v2'] = learning.curves[trial-1,'v2'] + learning.curves[trial-1,'deltav2']
  learning.curves[trial, 'deltav1'] = (l1 - learning.curves[trial,'v1']) * a1
  learning.curves[trial, 'deltav2'] = (l2 - learning.curves[trial,'v2']) * a2
}

learning.curves.v = pivot_longer(
  data = learning.curves[c('trial','lambda1','lambda2','alpha1','alpha2','v1','v2')],
  cols = c('v1','v2'),
  names_to = 'v'
)
learning.curves.v$v = factor(learning.curves.v$v)
learning.curves.v$v = recode(learning.curves.v$v, 'v1'='NT', 'v2'='T')


#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

p.learning.curves = ggplot(
  data = learning.curves.v,
  aes(x = trial, y = value, group = v, fill=v)
)

p.learning.curves + 
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = 21
  ) +
  
  scale_fill_manual(values=c('white','thistle4')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:trials) +

  ggtitle("Stimulus\nStrength") + ylab("% Freezing") + xlab("Day") +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TheoreticalSensitivity.tiff", sep = '_'))}


```



# Stats
## Novel Stressor
### Omnibus test
```{r}

novstressor.cs$subphase = as.character(novstressor.cs$subphase)
novsts.anova = ezANOVA(
  data = novstressor.cs,
  dv = freezing,
  wid = Animal,
  between = Group,
  within = c(subphase, component),
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)
novsts.anova

```

### Separate ANOVA on BL and CS
``` {r}

novstressor.cs$subphase = as.character(novstressor.cs$subphase)
novsts.bl.anova = ezANOVA(
  data = novstressor.cs[novstressor.cs$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = Group,
  within = c(subphase),
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)
novsts.bl.anova

novsts.cs.anova = ezANOVA(
  data = novstressor.cs[
    novstressor.cs$component=='cs',
    ],
  dv = freezing,
  wid = Animal,
  between = Group,
  within = c(subphase),
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)
novsts.cs.anova

```

### ANOVA for CS, excluding D1
```{r}

novsts.cs.nod1.anova = ezANOVA(
  data = novstressor.cs[
    novstressor.cs$component=='cs' & novstressor.cs$subphase!='1',
    ],
  dv = freezing,
  wid = Animal,
  between = Group,
  within = c(subphase),
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)
novsts.cs.nod1.anova


```



