---
title: "SEFL10e_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(
  fig.width=4.5, 
  fig.height=4.5, 
  echo=TRUE, 
  warning=FALSE,
  message=FALSE
  )
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
The data here comes from an initial pilot where mice initially received 150mg/mL anisomycin 15-20 minutes prior to trauma\
It was found that this high dose of anisomycin profoundly disrupted behavior during trauma, indicative of non-specific effects\
We subsequently used the NoTrauma-Veh and Trauma-Veh controls to test if\
A) This lower dose of anisomycin would effect trauma memory recall (in animals that previously received trauma and vehicle) \
B) This lower dose would effect fear memory formation (in animals that previously received no trauma and vehicle) \
C) This lower dose was able to block translation of cfos induced by shock \
Although the data from the initial behavior testing is provided, the analyses are not presented here for simplicity.
```{r}

#load 10e data 
data_vf = read.csv('sefl10e_vfdata.csv',header=TRUE)
groups = read.csv('sefl10e_groups.csv',header=TRUE)
fos = read.csv('sefl10e_fosdata.csv',header=TRUE)

#update group info
groups$Group = recode_factor(groups$Group, 'NT-Veh'='NT: veh', 'T-Veh'='T: veh', 'T-Ani'='T: Ani')
groups$ExpTest2_Drug = recode_factor(groups$ExpTest2_Drug, "ANI"='ani', "Veh"='veh')
groups$ExpTest2_Drug = factor(groups$ExpTest2_Drug, levels=c('veh','ani'))
groups$AcqTest_Drug = recode_factor(groups$AcqTest_Drug, "ANI"='ani', "Veh"='veh')
groups$AcqTest_Drug = factor(groups$AcqTest_Drug, levels=c('veh','ani'))
fos$ANI_Dose = as.factor(fos$ANI_Dose)

#add group info 
data_vf = right_join(x=groups,y=data_vf,by="Animal")

```



# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]

```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#Expression Test
exptest = data_vf[data_vf$phase=='ani_exp_test' & data_vf$component=='avg',]

#Acquisition Test
acq_acq = data_vf[data_vf$phase=='ani_acq' & data_vf$subphase!='shock',]
acq_recall = data_vf[data_vf$phase=='ani_acqtest' & data_vf$subphase=='avg',]
acq = rbind(acq_acq, acq_recall)
acq$subphase = factor(acq$subphase, c('bl','postshock','avg'))
acq$component = factor(acq$component, c('bl','postshock_01','postshock_02','postshock_03','avg'))

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#Expression
exptest.stats = summarise_at(
  .tbl = group_by(
    .data = exptest,
    ExpTest2_Drug, subphase, component),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)

#Acquisition
acq.stats = summarise_at(
  .tbl = group_by(
    .data = acq,
    AcqTest_Drug, subphase, component),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)

#cFOS
fos.stats = summarise_at(
  .tbl = group_by(
    .data = fos,
    ANI_Dose),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('Counts_PctControl')
)

```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10e'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =13
p.textsize.axis.title = 13
p.textsize.axis.text = 12
p.textsize.strip.text = 15

#Plot colors
p.scale.colour = c("white","red4",'paleturquoise4')
p.scale.fill = c("white","red4",'paleturquoise4')
#p.scale.fill = c("white","darkgray","royalblue4","red2",'darkgreen')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3.25, 2.45, 3.25), "cm") 
p.margin2 = unit(c(2, 3.75, 2.45, 3.75), "cm") 

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", size = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    strip.text = element_text(size=p.textsize.strip.text, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```



## Anisomycin effects

### Acquisition
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.acq = ggplot(
  data = acq.stats,
  aes(x=component,
      y=freezing_mean,
      fill=AcqTest_Drug,
      shape=AcqTest_Drug,
      group=interaction(subphase,AcqTest_Drug)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 60
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.acq  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','test')) +
  
  labs(
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_blank(),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      #face='plain',
      angle = 0,
      vjust=.5,
      hjust=.5),
    legend.position = c(.23,.9),
    plot.margin = p.margin1
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Acquisition.tiff", sep = '_'))}

```



### Expression
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.exp = ggplot(
  data = exptest.stats,
  aes(x=subphase,
      y=freezing_mean,
      fill=ExpTest2_Drug,
      group=ExpTest2_Drug))

#Define plot specific parameters
p.ymin = 0
p.ymax = 60
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.exp  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('test #1','test #2')) +
  
  labs(
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_blank(),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      #face='plain',
      angle = 0,
      vjust=.5,
      hjust=.5),
    legend.position = c(.23,.9),
    plot.margin = p.margin1
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Expression.tiff", sep = '_'))}

```


### Fos induction
```{r}

P.fos = ggplot(
  data = fos.stats,
  aes(x=ANI_Dose,
      y=mean,
      fill=ANI_Dose,
      group=ANI_Dose))

#Define plot specific parameters
p.ymin = 0
p.ymax = 160
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.fos  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    show.legend = FALSE,
    aes(ymin = mean - sem,
        ymax = mean + sem,
        #width = p.width.error
        )) +
  
  geom_jitter(
    data = fos,
    aes(x=ANI_Dose,
        y=Counts_PctControl),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('veh','ani')) +
  
  labs(
    y = "cFos (% veh)"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_blank(),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      #face='plain',
      angle = 0,
      vjust=.5,
      hjust=.5),
    legend.position = c(.23,.9),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Fos.tiff", sep = '_'))}

```


# Stats

## Expression
```{r}

exptest.anova = ezANOVA(
  data = exptest,
  wid = Animal,
  dv = freezing,
  within = subphase,
  between = ExpTest2_Drug,
  white.adjust = TRUE,
  type = 3,
  return_aov = FALSE,
  detailed = TRUE
)
exptest.anova

```


## Acquisition
```{r}

acq.bl.anova = ezANOVA(
  data = acq[acq$component=='bl',],
  wid = Animal,
  dv = freezing,
  between = AcqTest_Drug,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE,
  detailed = TRUE
)
acq.bl.anova

acq.postshock.anova = ezANOVA(
  data = acq[acq$subphase=='postshock',],
  wid = Animal,
  dv = freezing,
  within = component,
  between = AcqTest_Drug,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE,
  detailed = TRUE
)
acq.postshock.anova

acq.test.anova = ezANOVA(
  data = acq[acq$component=='avg',],
  wid = Animal,
  dv = freezing,
  between = AcqTest_Drug,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE,
  detailed = TRUE
)
acq.test.anova

```



## fos
```{r}

fos.anova = ezANOVA(
  data = fos,
  wid = Animal,
  dv = Counts_PctControl,
  between = ANI_Dose,
  white.adjust = TRUE,
  type = 3,
  return_aov = FALSE,
  detailed = TRUE
)
fos.anova

```





