---
title: "SEFL10e3_Retraining_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(
  fig.width=4.5, 
  fig.height=4.5, 
  echo=TRUE, 
  warning=FALSE,
  message=FALSE
  )
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
Note that here only effects of retraining subset of BLA animals given ani,\
relative to NT - Veh animals, is examined. Remaining results are examined combined \
with 10J.
```{r}

#load 10e3 data (cannulation of BLA)
s10e_vf = read.csv('SEFL10e3_vfdata.csv',header=TRUE)
s10e_vf$Animal = factor(paste(s10e_vf$Animal, '10e', sep='_'))

s10e_ld = read.csv('SEFL10e3_lddata.csv',header=TRUE)
s10e_ld$Animal = factor(paste(s10e_ld$Animal, '10e', sep='_'))

s10e_groups = read.csv('SEFL10e3_groups.csv',header=TRUE)
s10e_groups$region = 'BLA'
s10e_groups$Animal = factor(paste(s10e_groups$Animal, '10e', sep='_'))
s10e_groups$Group = as.character(s10e_groups$Group)
s10e_groups$Group[s10e_groups$Group=='T - ANI'] = 'T: ani'

#join datasets
groups = s10e_groups
groups$Group = recode(groups$Group, 'NT - Veh'='NT: veh', 'T - Veh'='T: veh')
groups$Group = factor(groups$Group, levels=c('NT: veh', 'T: veh', 'T: ani'))
data_vf = s10e_vf
data_vf = right_join(x=groups,y=data_vf,by="Animal")
data_ld = s10e_ld
data_ld = right_join(x=groups,y=data_ld,by="Animal")

remove(s10e_groups, s10e_ld, s10e_vf)

```



# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]

```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase,region, Group),
  .funs = list(motion=mean),
  .vars = c('motion')
)
trauma.shockreact$subphase[trauma.shockreact$subphase=='baseline'] = 'bl'


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]


#Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Group, region),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))


# retraining data
# a subset of BLA NT: veh and T: ani were given trauma and trauma test
# in order to assess impact on prior BLA ani on ability to learn associative memory
retrain = data_vf[data_vf$phase=='retrain' & data_vf$subphase!="shock",]
retrain_test = data_vf[data_vf$phase=='retrain_test' & data_vf$component=="avg",]

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma 
#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    region, component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    region, subphase,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    region, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    region, component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    region, component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    region, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    region, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('dark','Distance_in'))


#retrain trauma 
retrain.stats = summarise_at(
  .tbl = group_by(
    .data = retrain,
    subphase, region, component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
#recall
retrain_test.stats = summarise_at(
  .tbl = group_by(
    .data = retrain_test,
    region, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10e3_Retrain'

#ggsave
p.save = FALSE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12
p.textsize.strip.text = 15

#Plot colors
p.scale.colour = c("white","thistle4","#26466D","red4",'paleturquoise4')
p.scale.fill = c("white","thistle4","#26466D","red4",'paleturquoise4')
p.scale.colour.list = list(
  'BLA' = c("white","thistle4","#26466D","red4",'paleturquoise4'),
  'vHC' = c("white","thistle4","red4","#26466D",'paleturquoise4')
)
p.scale.fill.list = list(
  'BLA' = c("white","thistle4","#26466D","red4",'paleturquoise4'),
  'vHC' = c("white","thistle4","red4","#26466D",'paleturquoise4')
)


#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3.25, 1, 3.25), "cm")
p.margin2 = plot.margin = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma
p.margin4 = unit(c(1.2, 3, 1.7, 3), "cm")

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = .5,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    strip.text = element_text(size=p.textsize.strip.text, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```



### Retraining
#### trauma
```{r, fig.width=4.5, fig.height=4.5}

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

  
P.retrain = ggplot(
  data = retrain.stats,
  aes(
    x = component,
    y = freezing_mean,
    fill = Group,
    shape = Group,
    group = interaction(subphase,Group))) +

  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(
      ymin = freezing_mean - freezing_sem,
      ymax = freezing_mean + freezing_sem,
      width = p.width.error)) +
  
  geom_line(
    stat = "identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=c('white','red4')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size = p.textsize.axis.title-2,
      face = 'plain',
      angle = 0,
      vjust = .5),
    legend.position = c(.75,.15),
    plot.margin = p.margin3
  )

print(P.retrain)
if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Retrain.tiff", sep = '_'))}

```


#### recall
```{r, fig.width=4.5, fig.height=4.5}

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)


P.retrain_test = ggplot(
  data = retrain_test.stats,
  aes(
    x = Group,
    y = freezing_mean,
    fill = Group,
    group = Group)) +

  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = retrain_test,
    aes(x = Group, y = freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(
      ymin = freezing_mean - freezing_sem,
      ymax = freezing_mean + freezing_sem,
      width = p.width.error)) +
  
  scale_fill_manual(values=c('white','red4')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme

print(P.retrain_test)
if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "RetrainTest.tiff", sep = '_'))}


```



# Stats
### Retrain stats
```{r}

retrain.bl.anova = ezANOVA(
    data = retrain[retrain$subphase=='bl',],
    dv = freezing,
    wid = Animal,
    between = Group,
    white.adjust = TRUE,
    type = 3,
    return_aov = TRUE
  )
retrain.bl.anova

retrain.anova = ezANOVA(
    data = retrain[retrain$subphase!='bl',],
    dv = freezing,
    wid = Animal,
    between = Group,
    within = component,
    white.adjust = TRUE,
    type = 3,
    return_aov = TRUE
  )
retrain.anova

retrain_test.anova = ezANOVA(
  wid = Animal,
  data = retrain_test,
  dv = freezing,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE
)
retrain_test.anova

```








