---
title: "SEFL10j10e3_Combined_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(
  fig.width=4.5, 
  fig.height=4.5, 
  echo=TRUE, 
  warning=FALSE,
  message=FALSE
  )
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
Note that two experiments were combined in this analysis.\
Controls from each each experiment are compared to ensure lack of cohort effects.\
```{r}

#load 10e3 data (cannulation of BLA)
s10e_vf = read.csv('SEFL10e3_vfdata.csv',header=TRUE)
s10e_vf$region = 'BLA'
s10e_vf$Animal = factor(paste(s10e_vf$Animal, '10e', sep='_'))

s10e_ld = read.csv('SEFL10e3_lddata.csv',header=TRUE)
s10e_ld$region = 'BLA'
s10e_ld$Animal = factor(paste(s10e_ld$Animal, '10e', sep='_'))

s10e_groups = read.csv('SEFL10e3_groups.csv',header=TRUE)
s10e_groups$Animal = factor(paste(s10e_groups$Animal, '10e', sep='_'))
s10e_groups$Group = as.character(s10e_groups$Group)
s10e_groups$Group[s10e_groups$Group=='T - ANI'] = 'T: ani-BLA'


#load 10j data (cannulation of vHC)
s10j_vf = read.csv('SEFL10j_vfdata.csv',header=TRUE)
s10j_vf$region = 'vHC'
s10j_vf$Animal = factor(paste(s10j_vf$Animal, '10j', sep='_'))

s10j_ld = read.csv('SEFL10j_lddata.csv',header=TRUE)
s10j_ld$region = 'vHC'
s10j_ld$Animal = factor(paste(s10j_ld$Animal, '10j', sep='_'))

s10j_groups = read.csv('SEFL10j_groups.csv',header=TRUE)
s10j_groups$Animal = factor(paste(s10j_groups$Animal, '10j', sep='_'))
s10j_groups$Group = as.character(s10j_groups$Group)
s10j_groups$Group[s10j_groups$Group=='T - ANI'] = 'T: ani-vHC'


#join datasets
groups = bind_rows(s10e_groups, s10j_groups)
groups$Group = recode(groups$Group, 'NT - Veh'='NT: veh', 'T - Veh'='T: veh')
groups$Group = factor(groups$Group, levels=c('NT: veh', 'T: veh', 'T: ani-BLA', 'T: ani-vHC'))
data_vf = bind_rows(s10e_vf, s10j_vf)
data_vf = right_join(x=groups,y=data_vf,by="Animal")
data_ld = bind_rows(s10e_ld, s10j_ld)
data_ld = right_join(x=groups,y=data_ld,by="Animal")


```



# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]

```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Group),
  .funs = list(motion=mean),
  .vars = c('motion')
)
trauma.shockreact$subphase[trauma.shockreact$subphase=='baseline'] = 'bl'


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]


#Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Group, region),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))


#subsetted dataframes to compare controls
ctrl.ld =  ld.collapsed[ld.collapsed$Group!='T: ani-BLA' & ld.collapsed$Group != 'T: ani-vHC', ]
ctrl.traumatest =  traumatest[traumatest$Group!='T: ani-BLA' & traumatest$Group != 'T: ani-vHC', ]
ctrl.sefltest =  sefltest[sefltest$Group!='T: ani-BLA' & sefltest$Group != 'T: ani-vHC', ]

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma 
#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('dark','Distance_in'))


#Create dataframe to plot correlations between freezing at different points
freezing.df = right_join(
  traumatest[,c('Animal','Group','freezing')], sefltest[,c('Animal','freezing')],
  by = 'Animal', suffix = c("_traumatest","_sefltest"))
freezing.df = right_join(
  freezing.df, ld.collapsed[,c('Animal','dark')],
  by = 'Animal'
)


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10j10e3_combined'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("white","darkgray","royalblue4","red2",'darkgreen')
p.scale.fill = c("white","darkgray","royalblue4","red2",'darkgreen')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3, .35, 3), "cm")
p.margin2 = plot.margin = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", size = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```



## Anisomycin effects
Here, impacts of infusing anisomycin into the BLA/vHC after trauma are assessed.
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.75,.3),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



#### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Shock = ggplot(
  data = trauma.shockreact.stats,
  aes(x=subphase,
      y=mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Trauma\nShock Reactivity",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x= element_text(
      angle = 0,
      vjust=.5
    ),
    legend.position = c(.4,.85)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_ShockReact.tiff", sep = '_'))}


```


### Light-Dark
#### Dark-Time
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```


#### Distance Travelled
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dist = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=Distance_in_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 160
p.yint = 40
p.breaks = seq(p.ymin,p.ymax,p.yint)
p.dot.binwidth = 2

#Create plot
P.LD.dist  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=Distance_in),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_mean - Distance_in_sem,
        ymax = Distance_in_mean + Distance_in_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Light-Dark",
    x = "",
    y = "Distance (in/min)"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Distance.tiff", sep = '_'))}

```


### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Trauma",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```


### Novel Stressor
#### Startle Response
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Startle = ggplot(
  data = novstressor.startle.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Startle  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','startle','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.4,.85)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Startle.tiff", sep = '_'))}

```


#### Pre/Post Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Prepost = ggplot(
  data = novstressor.prepost.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Prepost  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    aes(fill = Group),
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','post')) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.35,.85)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Freezing.tiff", sep = '_'))}

```


### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest.tiff", sep = '_'))}

```


## Plot Control Data (vHC/BLA combined)
Control animals that received vehicle infusions are plotted for visualization of typical effects observed.
### Trauma Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.CTRL.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats[
    trauma.freezing.stats$Group=='NT: veh' | trauma.freezing.stats$Group=='T: veh',
  ],
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.CTRL.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.2,.9),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRL_Trauma.tiff", sep = '_'))}

```

### Light-Dark
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.CTRL.LD.dark = ggplot(
  data = ld.stats[
    ld.stats$Group=='NT: veh' |  ld.stats$Group=='T: veh',
  ],
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.CTRL.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed[
      ld.collapsed$Group=='NT: veh' |  ld.collapsed$Group=='T: veh',
    ],
    aes(x=Group,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  scale_x_discrete(labels=c('NT','T')) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x = element_text(angle=0),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRLLD_Dark.tiff", sep = '_'))}

```

### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.CTRL.TraumaTest = ggplot(
  data = traumatest.stats[
    traumatest.stats$Group=='NT: veh'|traumatest.stats$Group=='T: veh',
  ],
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.CTRL.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest[
      traumatest$Group=='NT: veh'|traumatest$Group=='T: veh',
    ],
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('NT','T')) +

  labs(
    #title = "Trauma Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x = element_text(angle=0),
    plot.margin = p.margin2
  )


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRLTraumaRecall.tiff", sep = '_'))}

```


### Novel Stressor BL
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.NS.baseline = ggplot(
  data = novstressor.prepost.stats[
    (
      novstressor.prepost.stats$Group=='NT: veh'| 
       novstressor.prepost.stats$Group=='T: veh'
    ) & novstressor.prepost.stats$component=='bl',
  ],
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)
  ) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.NS.baseline  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = novstressor.prepost[
      (novstressor.prepost$Group=='NT: veh'| novstressor.prepost$Group=='T: veh') &
      novstressor.prepost$component=='bl',
    ],
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('NT','T')) +
  
  labs(
    #title = "NS Baseline",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x = element_text(angle=0),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRLNSbaseline.tiff", sep = '_'))}

```

### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats[
    sefltest.stats$Group=='NT: veh'|sefltest.stats$Group=='T: veh',
  ],
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest[
      sefltest$Group=='NT: veh'|sefltest$Group=='T: veh',
    ],
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('NT','T')) +
  
  labs(
    #title = "Nov Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x = element_text(angle=0),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRLSEFLTest.tiff", sep = '_'))}

```


### Correlations for Trauma Controls
```{r, fig.width=4.5, fig.height=4.5, }

subdata = freezing.df[freezing.df$Group=='T: veh',]
subdata$dark = subdata$dark * 100

cor_list = list(
  c('freezing_traumatest', 'dark'),
  c('freezing_traumatest', 'freezing_sefltest'),
  c('dark', 'freezing_sefltest')
)
names(cor_list) = c('TrecLd', 'TrecSefl','LdSefl')

axis_titles = list(
  'freezing_traumatest' = 'Trauma Recall\n(% Freezing)',
  'dark' = 'Light-Dark\n(% Time in Dark)',
  'freezing_sefltest' = 'Novel Stressor\n(% Freezing)'
)

axis_scales = list(
  'freezing_traumatest' = seq(0, 100, 20),
  'dark' = seq(60, 100, 10),
  'freezing_sefltest' = seq(0, 40, 10)
)

cor_tests = list()
cor_plots = list()
x=3

for (i in 1:length(cor_list)){
  
  n = names(cor_list[i])
  pair = unlist(cor_list[i])

  cor_tests[[paste(pair[1], pair[2])]] = cor.test(
    x=subdata[,pair[1]], 
    y=subdata[,pair[2]],
    method = 'pearson'
  )
  
  c = cor_tests[[paste(pair[1], pair[2])]]
  
  xscale = unlist(axis_scales[pair[1]], use.names = FALSE)
  yscale = unlist(axis_scales[pair[2]], use.names = FALSE)
  
  cor_plots[[n]] = ggplot(
    data = subdata,
    aes_string(x = pair[1], y = pair[2])
  ) +

  geom_point(
    shape = 21,
    size = 3,
    color = 'black',
    fill = p.scale.fill[2],
    alpha = .8
  ) +
  
  scale_x_continuous(
    breaks = xscale,
    limits = c(min(xscale), max(xscale))
  ) +

  scale_y_continuous(
    breaks = yscale,
    limits = c(min(yscale), max(yscale))
  ) +

  labs(
    x = axis_titles[[pair[1]]],
    y = axis_titles[[pair[2]]],
    title = bquote(
      bold(R^.(as.character(2)) == ~ .(as.character(round(c$estimate^2,2)))) #~ " (n=40)"
    )
  ) +
  theme_classic() +
  theme(
    plot.title = element_text(hjust=.5, face='bold', size=p.textsize.title-3),
    axis.text = element_text(size=p.textsize.axis.text, color='black'),
    axis.title = element_text(face='bold', size=p.textsize.axis.title),
    plot.margin = unit(c('2.3','2.6','2.3','2.6'),'cm'),
    plot.background = element_rect(fill = "transparent",colour = NA)
  )
  
  if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "_CORR_", n, ".tiff", sep = ''))}
  print(cor_plots[[n]])
  
}



```


## Plot comparison of vHC/BLAcontrols
Control animals with cannula in vHC vs BLA are compared on main metrics.
#### Light-Dark
```{r}

#Create base layer from group level data
P.ctrls.LD.dark = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.ld,
      region,Group),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('dark','Distance_in')
  ),
  aes(
    x=region,
    y=dark_mean,
    fill=Group
  )
) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.ld,
    aes(x=region,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  facet_grid(cols=vars(var=Group)) +
  
  geom_hline(yintercept = .5, linetype='dashed') +

  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +

  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_LD_Dark.tiff", sep = '_'))}

```

#### Trauma recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.ctrls.traumatest = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.traumatest,
      region, Group),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('freezing','motion')
  ),
  aes(
    x=region,
    y=freezing_mean,
    fill=Group
  )
) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 80
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.traumatest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.traumatest,
    aes(x=region,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  facet_grid(cols=vars(var=Group)) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Trauma Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_TraumaRecall.tiff", sep = '_'))}

```


#### SEFL test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.ctrls.sefltest = ggplot(
  data = summarise_at(
    .tbl = group_by(
      .data = ctrl.sefltest,
      region,Group),
    .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
    .vars = c('freezing','motion')
  ),
  aes(
    x=region,
    y=freezing_mean,
    fill=Group
  )
) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 21
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.ctrls.sefltest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ctrl.sefltest,
    aes(x=region,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  facet_grid(cols=vars(var=Group)) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CtrlsONLY_SEFLTest.tiff", sep = '_'))}

```



# Stats
## Anisomycin effects
#### Contrast sets
Here, contrasts for a-prior comparisons is set.
```{r}

#a-prior comparisons
comparisons = list(
  c('T: veh', 'T: ani-BLA'),
  c('T: veh', 'T: ani-vHC'),
  c('T: ani-BLA', 'T: ani-vHC')
)

pcrit = 1 - (1 - .05)^(1/length(comparisons)) #Dunn-Sidak pcrit

```



#### SEFL Test Stats
```{r}

sefl.anova = ezANOVA(
  data = sefltest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  return_aov = TRUE,
  detailed = TRUE
)
sefl.anova


sefltest.posthoc = list()
for (comp in comparisons){
  sefltest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    sefltest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
sefltest.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```



#### Trauma Test Stats
```{r}

traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova


traumatest.posthoc = list()
for (comp in comparisons){
  traumatest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    traumatest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
traumatest.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```



#### Light Dark Stats
###### Dark side time
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova


ld.dark.posthoc = list()
for (comp in comparisons){
  ld.dark.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      dark[Group==comp[1]], dark[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
ld.dark.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```

##### Distance travelled
```{r}

#comparison of time in dark side
ld.dist.anova = ezANOVA(
  data = ld.collapsed,
  dv = Distance_in,
  wid = Animal,
  between = Group,
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dist.anova

ld.dist.posthoc = list()
for (comp in comparisons){
  ld.dist.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      Distance_in[Group==comp[1]], Distance_in[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
}
ld.dist.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```



## Control Data (vHC/BLA combined)
Comparisons of T vs NT for animals receiving vehicle.
#### LightDark
```{r}

ctrl.ld.dark.anova = ezANOVA(
  data = ctrl.ld,
  dv = dark,
  wid = Animal,
  between = c(Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.ld.dark.anova

```



#### Trauma recall
```{r}

ctrl.traumatest.anova = ezANOVA(
  data = ctrl.traumatest,
  dv = freezing,
  wid = Animal,
  between = c(Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.traumatest.anova

```



### Nov Stress bl
```{r}

#change to non-parametric or glm?

ctrl.novsts.anova = ezANOVA(
  data = novstressor.prepost[
    novstressor.prepost$component == 'bl' &
    (novstressor.prepost$Group=='NT: veh' | novstressor.prepost$Group=='T: veh'),
  ],
  dv = freezing,
  wid = Animal,
  between = c(Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.novsts.anova

```



### SEFL test
```{r}

ctrl.sefltest.anova = ezANOVA(
  data = ctrl.sefltest,
  dv = freezing,
  wid = Animal,
  between = c(Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.sefltest.anova

```


### Correlations
```{r}

cor_tests

```



## Comparison of VHC and BLA controls
Comparisons of BLA vs vHC controls.
#### LightDark
```{r}

ctrl.comp.ld.dark.anova = ezANOVA(
  data = ctrl.ld,
  dv = dark,
  wid = Animal,
  between = c(region,Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)

ctrl.comp.ld.dist.anova = ezANOVA(
  data = ctrl.ld,
  dv = Distance_in,
  wid = Animal,
  between = c(region,Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)

ctrl.comp.ld.dark.anova
ctrl.comp.ld.dist.anova

```



#### Trauma recall
```{r}

ctrl.comp.traumatest.anova = ezANOVA(
  data = ctrl.traumatest,
  dv = freezing,
  wid = Animal,
  between = c(region,Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.comp.traumatest.anova

```



### SEFL test
```{r}

ctrl.comp.sefltest.anova = ezANOVA(
  data = ctrl.sefltest,
  dv = freezing,
  wid = Animal,
  between = c(region,Group),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ctrl.comp.sefltest.anova

```




