---
title: "SEFL1c1d_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}

library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)

```



# Import Data 
Load  files and factorize as necessary.
Load  files and factorize as necessary.\
This analysis combines two studies (1C and 1D) of approximately equal n per group \
For 1D, a subset of mice were given 0.25 mA shocks and others 2 mA in order to compare amplitudes. \
Because 1 mA and 2 mA were generally comparable, 2 mA group is excluded here.\
EPM was also done at very end of study, though not reported in paper.
```{r}


# load 1d files
sefl1c_data_vf = read.csv('../SEFL1c_vfdata.csv',header=TRUE)
sefl1c_data_ld = read.csv('../SEFL1c_lddata.csv',header=TRUE)
sefl1c_data_epm = read.csv('../SEFL1C_epmdata.csv',header=TRUE)
sefl1c_ld = read.csv('../SEFL1c_lddata.csv',header=TRUE)
sefl1c_groups = read.csv('../SEFL1c_groups.csv',header=TRUE)
sefl1c_data_vf$EXP = '1c'
sefl1c_data_ld$EXP = '1c'
sefl1c_data_epm$EXP = '1c'
sefl1c_groups$EXP = '1c'


# load 1d files
sefl1d_data_vf = read.csv('../SEFL1d_vfdata.csv',header=TRUE)
sefl1d_data_ld = read.csv('../SEFL1d_lddata.csv',header=TRUE)
sefl1d_data_epm = read.csv('../SEFL1d_epmdata.csv',header=TRUE)
sefl1d_ld = read.csv('../SEFL1d_lddata.csv',header=TRUE)
sefl1d_groups = read.csv('../SEFL1d_groups.csv',header=TRUE)
sefl1d_data_vf$EXP = '1d'
sefl1d_data_ld$EXP = '1d'
sefl1d_data_epm$EXP = '1d'
sefl1d_groups$EXP = '1d'


#merge 1c and 1d
data_vf = bind_rows(sefl1c_data_vf, sefl1d_data_vf)
data_ld = bind_rows(sefl1c_data_ld, sefl1d_data_ld)
data_epm = bind_rows(sefl1c_data_epm, sefl1d_data_epm)
groups = bind_rows(sefl1c_groups, sefl1d_groups)


#make animal factor
groups = mutate(
  groups, AnimalID = paste(groups$Animal, AnimalID=groups$EXP, sep='_'), .after=Animal)
groups$Animal = groups$AnimalID
data_vf = mutate(
  data_vf, AnimalID = paste(data_vf$Animal, AnimalID=data_vf$EXP, sep='_'), .after=Animal)
data_vf$Animal = data_vf$AnimalID
data_ld = mutate(
  data_ld, AnimalID = paste(data_ld$Animal, AnimalID=data_ld$EXP, sep='_'), .after=Animal)
data_ld$Animal = data_ld$AnimalID
data_epm = mutate(
  data_epm, AnimalID = paste(data_epm$Animal, AnimalID=data_epm$EXP, sep='_'), .after=Animal)
data_epm$Animal = data_epm$AnimalID


#exclude highest shock amplitude
groups$Exclude[groups$Group=='T: 2.0 mA'] = 1
#groups$Exclude[groups$EXP=='1c'] = 1

#refactor groups
groups$Group = factor(groups$Group, levels=c('NT', 'T: Low', 'T: High'))


#add group info to data files
data_vf = right_join(x=groups,y=data_vf,by=c("Animal","AnimalID"))
data_ld = right_join(x=groups,y=data_ld,by=c("Animal","AnimalID"))
data_epm = right_join(x=groups,y=data_epm,by="Animal")

```




# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]
data_ld = data_ld[data_ld$Exclude!=1,]
data_epm = data_epm[data_epm$Exclude!=1,]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

# trauma data
## freezing
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]
## trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Sex, Group),
  .funs = list(motion=mean),
  .vars = c('motion')
)


# Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Sex, Group),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))
ld.collapsed$darkz = scale(ld.collapsed$dark)

#trauma test
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]


# Collapse epm post data
data_epm = data_epm[data_epm$bin<5,]
data_epm$closed = data_epm$c1 + data_epm$c2
epm.collapsed = summarize_at(
  .tbl = group_by(data_epm, Animal, Sex, Group),
  .funs = list(mean),
  .vars = c('closed','Distance_in'))


```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    subphase, component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)

trauma.freezing.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    subphase, component, Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)

trauma.shockreact.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n()), sd=~sd(.)),
  .vars = c('dark','Distance_in'))

ld.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n()), sd=~sd(.)),
  .vars = c('dark','Distance_in'))

#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

traumatest.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

novstressor.prepost.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component, Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

novstressor.startle.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component, Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

sefltest.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#epm post stats
epm.stats = summarise_at(
  .tbl = group_by(
    .data = epm.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n()), sd=~sd(.)),
  .vars = c('closed','Distance_in'))

epm.bysex.stats = summarise_at(
  .tbl = group_by(
    .data = epm.collapsed,
    Group, Sex),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n()), sd=~sd(.)),
  .vars = c('closed','Distance_in'))


#Create dataframe to plot correlations between freezing at different points
freezing.df = right_join(
  traumatest[,c('Animal','Sex','Group','freezing')], sefltest[,c('Animal','freezing')],
  by = 'Animal', suffix = c("_traumatest","_sefltest"))
freezing.df = right_join(
  freezing.df, ld.collapsed[,c('Animal','dark')],
  by = 'Animal'
)
freezing.df = right_join(
  freezing.df, epm.collapsed[,c('Animal','closed')],
  by = 'Animal'
)



```


# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '1C1D_AMP'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("gray28",'gray74',"gray100")
p.scale.fill = c("gray28",'gray74',"gray100")
p.scale.fill.sex = c("steelblue4",'red3')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .7
p.width.jitter = .3
p.width.error = .5


#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2
p.dot.shape = 21
p.dot.alpha = .7

#p.margin
p.margin1 = unit(c(2, 3.25, 1.1, 3.25), "cm")
p.margin2 = unit(c(1.25, 2.25, 2.15, 2.25), "cm") # for sex comparisons
p.margin3 = unit(c(2, 3., 2.45, 3.), "cm") #for trauma
p.margin4 = unit(c(1.25, .45, 2.45, .05), "cm") #for trauma by sex

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    strip.text = element_text(size=p.textsize.title-5, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    #colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape
  ) +
  
  #scale_shape_manual(values=p.point.shape) +
  #scale_shape_manual(values=c(21,24)) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(
    labels=c('bl','1','2','3','4','5','6','7','8','9','10'),
    expand = c(.08,.08)
    ) +
  
  labs(
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      hjust = .5,
      vjust=.5),
    legend.position = c(.3, .87),
    #legend.direction = 'horizontal',
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```

##### Freezing by sex
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing.bysex = ggplot(
  data = trauma.freezing.bysex.stats,
  aes(x=component,
      y=freezing_mean,
      color=Sex,
      fill =Group,
      group=interaction(subphase,Sex,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing.bysex  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    color='black',
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    color='black',
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape,
    show.legend = FALSE
  ) +
  
  #facet_grid(cols=vars(Group)) +
  
  #scale_shape_manual(values=p.point.shape) +
  #scale_shape_manual(values=c(21,24)) +
  scale_color_manual(values=p.scale.fill.sex) +
  scale_fill_manual(values=p.scale.fill) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.2,.9),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_bysex.tiff", sep = '_'))}

```

### Light-Dark
#### Dark-Time
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.03
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        color=Sex,
        y=dark),
    shape = 1,
    stroke = .5,
    width = p.width.bar* p.width.jitter,
    height = 0,
    size = p.dot.size,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_color_manual(values=p.scale.fill.sex) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  #facet_grid(cols=vars(Sex)) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```


##### Dark-Time by sex
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark.bysex = ggplot(
  data = ld.bysex.stats,
  aes(x=Sex,
      y=dark_mean,
      fill=Sex,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark.bysex  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Sex,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  facet_grid(cols=vars(Group)) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.fill.sex) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme +
  theme(
    plot.margin = p.margin2,
    axis.text.x = element_text(angle=0, hjust=.5)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark_bysex.tiff", sep = '_'))}

```



### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Group,
        color=Sex,
        y=freezing),
    shape = 1,
    stroke = .5,
    width = p.width.bar* p.width.jitter,
    height = 0,
    size = p.dot.size,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_color_manual(values=p.scale.fill.sex) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```

#### Trauma Recall by sex
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest.bysex = ggplot(
  data = traumatest.bysex.stats,
  aes(x=Sex,
      y=freezing_mean,
      fill=Sex,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest.bysex  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Sex,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  facet_grid(cols=vars(Group)) +
  
  scale_fill_manual(values=p.scale.fill.sex) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.margin = p.margin2,
    axis.text.x = element_text(angle=0, hjust=.5)
  )


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall_bysex.tiff", sep = '_'))}

```

### Novel Stressor
#### Startle Response
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Startle = ggplot(
  data = novstressor.startle.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Startle  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','startle','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.4,.85)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NovStressor_Startle.tiff", sep = '_'))}

```


#### Novel Stressor BL
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.NS.baseline = ggplot(
  data = novstressor.prepost.stats[novstressor.prepost.stats$component=='bl',],
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)
  ) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 32
p.yint = 10
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.NS.baseline  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = novstressor.prepost[novstressor.prepost$component=='bl',],
    aes(x=Group,
        color=Sex,
        y=freezing),
    shape = 1,
    stroke = .5,
    width = p.width.bar* p.width.jitter,
    height = 0,
    size = p.dot.size,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  scale_color_manual(values=p.scale.fill.sex) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "NS Baseline",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    #axis.text.x = element_text(angle=0),
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "NSbaseline.tiff", sep = '_'))}

```


### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 32
p.yint = 10
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Group,
        color=Sex,
        y=freezing),
    shape = 1,
    stroke = .5,
    width = p.width.bar* p.width.jitter,
    height = 0,
    size = p.dot.size,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_color_manual(values=p.scale.fill.sex) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
    theme(
      #axis.text.x = element_text(angle=0, hjust=.5),
      axis.text.y = element_text(color='white'),
      axis.title = element_text(color='white')
    )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest.tiff", sep = '_'))}

```


#### SEFL Test by sex
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest.bysex = ggplot(
  data = sefltest.bysex.stats,
  aes(x=Sex,
      y=freezing_mean,
      fill=Sex,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 32
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest.bysex  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Sex,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.fill.sex) +
  
  facet_grid(cols = vars(Group)) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.margin = p.margin2,
    axis.text.x = element_text(angle=0, hjust=.5)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest_bysex.tiff", sep = '_'))}

```


### EPM Post Nov Stressor
#### Closed arms
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.EPMpost.dark = ggplot(
  data = epm.stats,
  aes(x=Group,
      y=closed_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.EPMpost.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = closed_mean - closed_sem,
        ymax = closed_mean + closed_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = epm.collapsed,
    aes(x=Group,
        y=closed),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Closed"
  ) +
  
  #facet_grid(cols=vars(Sex)) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "EPMpost_Dark.tiff", sep = '_'))}

```

##### Closed arms by sex
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark.bysex = ggplot(
  data = epm.bysex.stats,
  aes(x=Sex,
      y=closed_mean,
      fill=Sex,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark.bysex  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = closed_mean - closed_sem,
        ymax = closed_mean + closed_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = epm.collapsed,
    aes(x=Sex,
        y=closed),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  facet_grid(cols=vars(Group)) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.fill.sex) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Closed"
  ) +
  
  p.basetheme +
  theme(
    plot.margin = p.margin2,
    axis.text.x = element_text(angle=0, hjust=.5)
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark_bysex.tiff", sep = '_'))}

```



# Stats

## Contrast sets
Here, contrasts for a-prior comparisons is set.
Currently, all planned comparisons performed independent of omnibus because of 
heteroscedasticity. Comparisons were performed using both Welch procedure and
hccm standard errors and rendered the same pattern of results.
```{r}

#a-prior comparisons
comparisons = list(
  c('NT', 'T: Low'),
  c('T: Low', 'T: High')
)

pcrit = 1 - (1 - .05)^(1/(length(comparisons))) #Dunn-Sidak pcrit

#function to perform hccm coefficient tests
coeftest.hccm = function(linmod) {
  tests = coeftest(linmod, hccm(linmod, 'hc3'))
  return(list('tests'=tests, 'df'=linmod$df.residual))
}

```

## Trauma Stats
```{r}

#comparison of all groups' freezing
trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = .(Group, Sex),
  type = 3,
  detailed = TRUE
)
trauma.fz.anova


#comparison of trauma animals' freezing
trauma.tonly.fz.anova = ezANOVA(
  data = trauma.freezing[trauma.freezing$Group!="NT",],
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = .(Group, Sex),
  type = 3,
  detailed = TRUE
)
trauma.tonly.fz.anova

```

## Light-Dark
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova

ld.dark.posthoc = list()
ld.dark.hccm.posthoc = list()
for (comp in comparisons){
  ld.dark.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      dark[Group==comp[1]], dark[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
  linmod = lm(
    dark~Group, 
    data = ld.collapsed,
    subset = ld.collapsed$Group==comp[1] | ld.collapsed$Group==comp[2]
  )
  ld.dark.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
ld.dark.posthoc
#ld.dark.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```


## Trauma Recall
```{r}

#comparison of time in dark side
traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova

traumatest.posthoc = list()
traumatest.hccm.posthoc = list()
for (comp in comparisons){
  traumatest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    traumatest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
  
  linmod = lm(
    freezing~Group, 
    data = traumatest,
    subset = traumatest$Group==comp[1] | traumatest$Group==comp[2]
  )
  traumatest.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
traumatest.posthoc
#traumatest.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))


```


## SEFL test
### BL
```{r}

novstressorBL.anova = ezANOVA(
  data = novstressor.prepost[novstressor.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = FALSE, #couldn't fit with white.adjust set to TRUE
  type = 3,
  detailed = TRUE
)
novstressorBL.anova

```

### sefl test
```{r}

#comparison of time in dark side
sefltest.anova = ezANOVA(
  data = sefltest,
  dv = freezing,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
sefltest.anova

sefltest.posthoc = list()
sefltest.hccm.posthoc = list()
for (comp in comparisons){
  sefltest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    sefltest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    )
  )
  linmod = lm(
    freezing~Group, 
    data = sefltest,
    subset = sefltest$Group==comp[1] | sefltest$Group==comp[2]
  )
  sefltest.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}

sefltest.posthoc
#sefltest.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```


## EPM
```{r}

#comparison of time in closed side
epm.closed.anova = ezANOVA(
  data = epm.collapsed,
  dv = closed,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
epm.closed.anova


```



