---
title: "SEFL10g2g3_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.\
This analysis combines two studies of approximately equal n per group \
For 10g2, all mice received 3 injections beginning immediately after trauma (either saline or anisomycin).\
For 10g3, all mice received 6 injections: 3 beginning just after trauma (spaced 4h apart), and 3 beginning 48 hr after trauma (again, spaced 4 hrs apart). \
Anisomycin animals either were treated anisomycin during the first 3 injections and saline for the second, or vice versa. \
Note that for 10g2 some mice received 2 injections of anisomycin (3rd injection is saline), these animals are excluded here
```{r}

# load 10g2 files
g2data_vf = read.csv('SEFL10g2_vfdata.csv',header=TRUE)
g2data_ld = read.csv('SEFL10g2_lddata.csv',header=TRUE)
g2groups = read.csv('SEFL10g2_groups.csv',header=TRUE)

g2data_vf$EXP = 'g2'
g2data_ld$EXP = 'g2'
g2groups$EXP = 'g2'

g2groups$Group = factor(g2groups$Group, levels=c('NT - Veh', 'T - ANI 2x', 'T - Veh', 'T - ANI 3x'))
g2groups$Group = recode_factor(
  g2groups$Group,
  'NT - Veh'= 'NT: veh',
  'T - Veh' = 'T: veh',
  'T - ANI 2x' = 'T - ANI 2x',
  'T - ANI 3x' = 'T: ani (0h)'
  )


#load 10g3 files
g3data_vf = read.csv('SEFL10g3_vfdata.csv',header=TRUE)
g3data_ld = read.csv('SEFL10g3_lddata.csv',header=TRUE)
g3groups = read.csv('SEFL10g3_groups.csv',header=TRUE)

g3data_vf$EXP = 'g3'
g3data_ld$EXP = 'g3'
g3groups$EXP = 'g3'

g3groups$Group = factor(g3groups$Group, levels = c('NT: veh','T: veh','T: ani (imm.)','T: ani (del.)'))
g3groups$Group = recode_factor(
  g3groups$Group, 
  'NT: veh'='NT: veh',
  'T: veh'='T: veh',
  'T: ani (imm.)' = 'T: ani (0h)',
  'T: ani (del.)' = 'T: ani (48h)'
  )


#merge 10g2 and 10g3
data_vf = bind_rows(g2data_vf, g3data_vf)
data_ld = bind_rows(g2data_ld, g3data_ld)
groups = bind_rows(g2groups, g3groups)

#make animal factor
groups = mutate(
  groups, AnimalID = paste0(groups$Animal, AnimalID=groups$EXP, sep=''), .after=Animal)
groups$Animal = groups$AnimalID
data_vf = mutate(
  data_vf, AnimalID = paste0(data_vf$Animal, AnimalID=data_vf$EXP, sep=''), .after=Animal)
data_vf$Animal = data_vf$AnimalID
data_ld = mutate(
  data_ld, AnimalID = paste0(data_ld$Animal, AnimalID=data_ld$EXP, sep=''), .after=Animal)
data_ld$Animal = data_ld$AnimalID

#add group info to data files
data_vf = right_join(x=groups,y=data_vf,by=c("Animal","AnimalID","EXP"))
data_ld = right_join(x=groups,y=data_ld,by=c("Animal","AnimalID","EXP"))

```




# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Group!='T - ANI 2x',]
data_ld = data_ld[data_ld$Group!='T - ANI 2x',]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

# trauma data
## freezing
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]
## trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Sex, Group, EXP),
  .funs = list(motion=mean),
  .vars = c('motion')
)


# Collapse ld data
data_ld = data_ld[data_ld$bin<5,]
ld.collapsed = summarize_at(
  .tbl = group_by(data_ld, Animal, Sex, Group, Trauma, EXP),
  .funs = list(mean),
  .vars = c('dark','Distance_in'))


#trauma test
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='mildstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))


#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]



```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    subphase, component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)


#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#ld stats
ld.stats = summarise_at(
  .tbl = group_by(
    .data = ld.collapsed,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n()), sd=~sd(.)),
  .vars = c('dark','Distance_in'))


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)

#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component, Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)



#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)




```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10g2g3'

#ggsave
p.save = FALSE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12
p.textsize.strip.text = 15

#Plot colors
p.scale.colour = c("gray28","white",'green4','yellow2')
p.scale.fill =  c("gray28","white",'green4','yellow2')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .7
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .25

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3, .225, 3), "cm")
p.margin2 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 90
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    #colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.9,.3),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



### Light-Dark
#### Dark-Time
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dark = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=dark_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = .4
p.ymax = 1.02
p.yint = .2
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.LD.dark  +
  
  geom_crossbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = dark_mean - dark_sem,
        ymax = dark_mean + dark_sem),
    width = p.width.bar,
    show.legend = FALSE) +
  
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=dark),
    width = p.width.bar* p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_hline(yintercept = .5, linetype='dashed') +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, labels = p.breaks*100, expand = c(0, 0)) +
  
  labs(
    #title = "Light-Dark",
    x = "",
    y = "% Time in Dark"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Dark.tiff", sep = '_'))}

```





#### Distance Travelled
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.LD.dist = ggplot(
  data = ld.stats,
  aes(x=Group,
      y=Distance_in_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 200
p.yint = 40
p.breaks = seq(p.ymin,p.ymax,p.yint)
p.dot.binwidth = 2

#Create plot
P.LD.dist  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = ld.collapsed,
    aes(x=Group,
        y=Distance_in),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = .5,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = Distance_in_mean - Distance_in_sem,
        ymax = Distance_in_mean + Distance_in_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    #title = "Light-Dark",
    x = "",
    y = "Distance (in/min)"
  ) +
  
  p.basetheme

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "LD_Distance.tiff", sep = '_'))}

```


### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = traumatest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```


### Novel Stressor
#### Startle Response
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Startle = ggplot(
  data = novstressor.startle.stats,
  aes(x=component,
      y=motion_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Startle  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = motion_mean - motion_sem,
        ymax = motion_mean + motion_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','startle','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  c(.4,.85)
  )

```


#### Pre/Post Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.MS.Prepost = ggplot(
  data = novstressor.prepost.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 40
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.MS.Prepost  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    aes(fill = Group  ),
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  scale_x_discrete(labels=c('bl','post')) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    legend.position =  'top'
  )


```

#### Novel Stressor BL
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.NS.baseline = ggplot(
  data = novstressor.prepost.stats[novstressor.prepost.stats$component=='bl',],
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)
  ) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 26
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.NS.baseline  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = novstressor.prepost[novstressor.prepost$component=='bl',],
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values = p.scale.fill , labels=(c('NT','T'))) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  #scale_x_discrete(labels=c('NT','T')) +
  
  labs(
    #title = "NS Baseline",
    x = "",
    y = "% Freezing",
  ) +
  
  p.basetheme +
  theme(
    #axis.text.x = element_text(angle=0),
    #plot.margin = p.margin2
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "CTRLNSbaseline.tiff", sep = '_'))}

```


### SEFL Test
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.SEFLTest = ggplot(
  data = sefltest.stats,
  aes(x=Group,
      y=freezing_mean,
      fill=Group,
      group=Group)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 27
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.SEFLTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
  geom_jitter(
    data = sefltest,
    aes(x=Group,
        y=freezing),
    width = p.width.bar * p.width.jitter,
    height = 0,
    shape = p.dot.shape,
    size = p.dot.size,
    colour = 'black',
    fill=NA,
    alpha = p.dot.alpha,
    show.legend=FALSE
  ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.fill) +
  
  #facet_grid(cols = vars(Sex)) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Novel Stressor Recall",
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "SEFLTest.tiff", sep = '_'))}

```





# Stats
## Contrast sets
Here, contrasts for a-prior comparisons is set.
Currently, all planned comparisons performed independent of omnibus because of 
heteroscedasticity. Comparisons were performed using both Welch procedure and
hccm standard errors and rendered the same pattern of results.
```{r}

#a-prior comparisons
comparisons = list(
  c('NT: veh', 'T: veh'),
  c('T: veh', 'T: ani (0h)'),
  c('T: veh', 'T: ani (48h)')
)

pcrit = 1 - (1 - .05)^(1/length(comparisons)) #Dunn-Sidak pcrit

#function to perform hccm coefficient tests
coeftest.hccm = function(linmod) {
  tests = coeftest(linmod, hccm(linmod, 'hc3'))
  return(list('tests'=tests, 'df'=linmod$df.residual))
}

```


## Trauma Stats
```{r}

#comparison of trauma animals' freezing
trauma.fz.anova = ezANOVA(
  data = trauma.freezing[trauma.freezing$Group!="NT: veh",],
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = .(Group, Sex),
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```

## Light-Dark
```{r}

#comparison of time in dark side
ld.dark.anova = ezANOVA(
  data = ld.collapsed,
  dv = dark,
  wid = Animal,
  between = .(Group, Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
ld.dark.anova

ld.dark.posthoc = list()
ld.dark.hccm.posthoc = list()
for (comp in comparisons){
  ld.dark.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    ld.collapsed,
    t.test(
      dark[Group==comp[1]], dark[Group==(comp)[2]],
      var.equal = FALSE
    ))
  linmod = lm(
    dark~Group, 
    data = ld.collapsed,
    subset = ld.collapsed$Group==comp[1] | ld.collapsed$Group==comp[2]
  )
  ld.dark.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
ld.dark.posthoc
#ld.dark.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```


## Trauma Recall
```{r}

#comparison of time in dark side
traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = .(Group,Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova


traumatest.posthoc = list()
traumatest.hccm.posthoc = list()
for (comp in comparisons){
  traumatest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    traumatest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    ))
  linmod = lm(
    freezing~Group, 
    data = traumatest,
    subset = traumatest$Group==comp[1] | traumatest$Group==comp[2]
  )
  traumatest.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
traumatest.posthoc
#traumatest.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```


## SEFL Test
```{r}

#comparison of time in dark side
sefltest.anova = ezANOVA(
  data = sefltest,
  dv = freezing,
  wid = Animal,
  between = .(Group,Sex),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
sefltest.anova


sefltest.posthoc = list()
sefltest.hccm.posthoc = list()
for (comp in comparisons){
  sefltest.posthoc[[paste(comp[1], 'vs', comp[2])]] = with(
    sefltest,
    t.test(
      freezing[Group==comp[1]], freezing[Group==(comp)[2]],
      var.equal = FALSE
    ))
  linmod = lm(
    freezing~Group, 
    data = sefltest,
    subset = sefltest$Group==comp[1] | sefltest$Group==comp[2]
  )
  sefltest.hccm.posthoc[[paste(comp[1], 'vs', comp[2])]] = coeftest.hccm(linmod)
}
sefltest.posthoc
#sefltest.hccm.posthoc
paste('critical for multiple comparisons: ', round(pcrit, 4))

```





