---
title: "SEFL1F_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary.
```{r}

#load  files
data_vf = read.csv('SEFL1F_vfdata.csv',header=TRUE)
groups = read.csv('SEFL1F_groups.csv',header=TRUE)


#make animal factor
groups$Animal = factor(groups$Animal)
data_vf$Animal = factor(data_vf$Animal)


#add group info to data files
data_vf = right_join(x=groups,y=data_vf,by="Animal")

```




# Drop excluded subjects
See `groups` dataframe for exclusion rationale.
Note that there were 2 animals that generalized slighly when first placed in 
environment of novel stressor (~10%). If these animals are excluding, the same
pattern of results is observed.
```{r}

#data_vf = data_vf[data_vf$Exclude!=1,]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

# trauma data
## freezing
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]
## trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal,subphase, Trauma),
  .funs = list(motion=mean),
  .vars = c('motion')
)


#trauma test
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$subphase=='avg',]


#weakshock data
##prepost startle stimulus
wshock.prepost = data_vf[data_vf$phase=='weakshock' & data_vf$subphase=='prepost',]
wshock.prepost$component = factor(wshock.prepost$component, levels=c('bl','post'))

##startle response
wshock.startle = data_vf[data_vf$phase=='weakshock' & data_vf$subphase=='shock',]
wshock.startle$component = factor(
  wshock.startle$component,
  levels=c('shock_pre','shock_shock','shock_post'))
wshock.startle = summarise_at(
  .tbl = group_by(
    .data = wshock.startle,
    Animal, Trauma, component),
  .funs = list(motion=mean),
  .vars = c('motion')
)

#define each animal's asymptote
wshock.asym = summarise_at(
  .tbl = group_by(
    .data = wshock.prepost[
      wshock.prepost$component=='bl' & wshock.prepost$day>2,
      ],
    Animal),
  .funs = list(asym=mean),
  .vars = c('freezing')
)
wshock.prepost = right_join(wshock.prepost, wshock.asym, by='Animal')

#define freezing as pct asymptote
wshock.prepost$pctasym = (wshock.prepost$freezing / wshock.prepost$asym)*100

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    subphase, component, Trauma),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Trauma),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Trauma),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#weak shock
#pre/post
wshock.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = wshock.prepost,
    #day, component, Trauma, Batch),
    day, component, Trauma),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion','pctasym')
)

#weak shock startle
wshock.startle.stats = summarise_at(
  .tbl = group_by(
    .data = wshock.startle,
    component, Trauma),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


```


# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '1F'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 18
p.textsize.legend =13
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("gray28","gray100")
p.scale.fill = c("gray28","gray100")
p.scale.fill.sex = c("white",'blue3')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .7
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .25


#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = plot.margin = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin2 = unit(c(2, 3.25, 2.45, 3.25), "cm") 
p.margin3 =  unit(c(1.3, 3.5, 1.45, 3.5), 'cm')
p.margin4 =  unit(c(1.3, 4, 1.45, 4), 'cm')

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", size = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=12,t=0), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.title.x = element_text(margin=margin(t=-1)),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='plain',
      angle = 0,
      vjust=.5,
      margin = margin(b=10,t=5)
      ),
    legend.position = 'right',
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Trauma,
      group=interaction(subphase,Trauma)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape
  ) +
  
  #scale_shape_manual(values=p.point.shape) +
  scale_shape_manual(values=c(21,24)) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.2, .9),
    plot.margin = p.margin2
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



#### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Shock = ggplot(
  data = trauma.shockreact.stats,
  aes(x=subphase,
      y=mean,
      fill=Trauma,
      group=Trauma)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke,
    show.legend = FALSE
  ) +
  
  scale_shape_manual(values=c(21,24)) +
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    legend.position = c(.4,.85),
    plot.margin = p.margin2
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_ShockReact.tiff", sep = '_'))}


```



### Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Trauma,
      y=freezing_mean,
      fill=Trauma,
      group=Trauma)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
    geom_jitter(
      data = traumatest,
      aes(x=Trauma,
          y=freezing),
      width = p.width.bar * p.width.jitter,
      height = 0,
      shape = p.dot.shape,
      size = p.dot.size,
      colour = 'black',
      fill=NA,
      alpha = p.dot.alpha,
      show.legend=FALSE
    ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}

```


### Weak Shock

#### Day 1
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.wshock1 = ggplot(
  data = wshock.prepost.stats[
    wshock.prepost.stats$day==1 & wshock.prepost.stats$component=='bl',
    ],
  aes(x=Trauma,
      y=freezing_mean,
      fill=Trauma,
      group=Trauma)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 30
p.yint = 10
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.wshock1  +
  
  geom_bar(
    stat="identity",
    colour = 'black',
    position=position_dodge(),
    size=p.line.bar.size,
    width=p.width.bar,
    show.legend = FALSE) +
  
    geom_jitter(
      data = wshock.prepost[
        wshock.prepost$day==1 & wshock.prepost$component=='bl',
        ],
      aes(x=Trauma,
          y=freezing),
      width = p.width.bar * p.width.jitter,
      height = 0,
      shape = p.dot.shape,
      size = p.dot.size,
      colour = 'black',
      fill=NA,
      alpha = p.dot.alpha,
      show.legend=FALSE
    ) +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error)) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +

  labs(
    x = "",
    y = "% Freezing"
  ) +
  
  p.basetheme 


#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Wshock1.tiff", sep = '_'))}

```

#### BL Freezing
```{r, fig.width=4.5, fig.height=4.5}


component = 'bl'

#Create base layer from group level data
P.wshock.bl = ggplot(
  data = wshock.prepost.stats[
    wshock.prepost.stats$component==component,
  ],
  aes(x=day,
      y=freezing_mean,
      fill=Trauma,
      group=Trauma))

#Define plot specific parameters
p.ymin = 0
p.ymax = 20
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.wshock.bl  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    #colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape,
    show.legend = FALSE
  ) +

  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:7, expand = c(0,.5)) +
  
  labs(
    title = "\n",
    x = "Day",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     axis.text.x = element_text(angle=0, face='plain'),
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "WshockBl.tiff", sep = '_'))}

```


#### BL Freezing (Pct Asymptote)
```{r, fig.width=4.5, fig.height=4.5}


component = 'bl'

#Create base layer from group level data
P.wshock.pctbl = ggplot(
  data = wshock.prepost.stats[
    wshock.prepost.stats$component==component,
  ],
  aes(x=day,
      y=pctasym_mean,
      fill=Trauma,
      group=Trauma))

#Define plot specific parameters
p.ymin = 0
p.ymax = 130
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.wshock.pctbl  +
  
  geom_hline(yintercept = 100, linetype='dashed') +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    #colour = "black",
    aes(ymin = pctasym_mean - pctasym_sem,
        ymax = pctasym_mean + pctasym_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape,
    show.legend = FALSE
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:7, expand = c(0,.5)) +
  
  labs(
    title = "\n",
    x = "Day",
    y = "Freezing (% Asymptote)"
  ) +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     axis.text.x = element_text(angle=0, face='plain'),
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "WshockPct.tiff", sep = '_'))}

```

#### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.wshock.shock = ggplot(
  data = wshock.startle.stats[wshock.startle.stats$component!='shock_post',],
  aes(x=component,
      y=mean,
      fill=Trauma,
      group=Trauma))

#Define plot specific parameters
p.ymin = 0
p.ymax = 500
p.yint = 100
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.wshock.shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    #colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = p.point.shape,
    show.legend = FALSE
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','shock')) +
  
  labs(
    title = "\n",
    x = "",
    y = "Shock Reactivity (au)"
  ) +
  
  p.basetheme +
  theme(
    axis.title.x = element_text(margin=margin(b=.5)),
    axis.text.x= element_text(
      #size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      hjust=.5),
    legend.position = 'top',
    legend.direction = 'horizontal',
    plot.margin = p.margin4
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "ShockReactivity.tiff", sep = '_'))}

```

## Theoretical curves
Below, simulated examples of learning rate vs stimulus strength changes using Rescorla Wagner are plotted presented.
### Learning Rate
```{r}

trials = 7
l1 = 15
l2 = 15
a1 = .375
a2 = .9

learning.curves = data.frame(
  'trial' = seq(1,trials,1),
  'lambda1' = rep(l1, trials),
  'lambda2' = rep(l2, trials),
  'alpha1' = rep(a1, trials),
  'alpha2' = rep(a2, trials),
  'deltav1' = rep((l1-0)*a1, trials),
  'deltav2' = rep((l2-0)*a2, trials),
  'v1' = rep(0, trials),
  'v2' = rep(0, trials)
)

for (trial in 2:trials) {
  learning.curves[trial, 'v1'] = learning.curves[trial-1,'v1'] + learning.curves[trial-1,'deltav1']
  learning.curves[trial, 'v2'] = learning.curves[trial-1,'v2'] + learning.curves[trial-1,'deltav2']
  learning.curves[trial, 'deltav1'] = (l1 - learning.curves[trial,'v1']) * a1
  learning.curves[trial, 'deltav2'] = (l2 - learning.curves[trial,'v2']) * a2
}

learning.curves.v = pivot_longer(
  data = learning.curves[c('trial','lambda1','lambda2','alpha1','alpha2','v1','v2')],
  cols = c('v1','v2'),
  names_to = 'v'
)
learning.curves.v$v = factor(learning.curves.v$v)
learning.curves.v$v = recode(learning.curves.v$v, 'v1'='NT', 'v2'='T')


#Define plot specific parameters
p.ymin = 0
p.ymax = 20
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

p.learning.curves = ggplot(
  data = learning.curves.v,
  aes(x = trial, y = value, group = v, fill=v)
)

p.learning.curves + 
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = 21
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:trials, expand = c(0,.5)) +
  
  ggtitle("Learning\nRate") + ylab("% Freezing") + xlab("Day") +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     axis.text.x = element_text(angle=0, face='plain'),
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TheoreticalRate.tiff", sep = '_'))}


```


### Stim Strength
```{r}


trials = 7
l1 = 7.5
l2 = 15
a1 = .9
a2 = .9

learning.curves = data.frame(
  'trial' = seq(1,trials,1),
  'lambda1' = rep(l1, trials),
  'lambda2' = rep(l2, trials),
  'alpha1' = rep(a1, trials),
  'alpha2' = rep(a2, trials),
  'deltav1' = rep((l1-0)*a1, trials),
  'deltav2' = rep((l2-0)*a2, trials),
  'v1' = rep(0, trials),
  'v2' = rep(0, trials)
)

for (trial in 2:trials) {
  learning.curves[trial, 'v1'] = learning.curves[trial-1,'v1'] + learning.curves[trial-1,'deltav1']
  learning.curves[trial, 'v2'] = learning.curves[trial-1,'v2'] + learning.curves[trial-1,'deltav2']
  learning.curves[trial, 'deltav1'] = (l1 - learning.curves[trial,'v1']) * a1
  learning.curves[trial, 'deltav2'] = (l2 - learning.curves[trial,'v2']) * a2
}

learning.curves.v = pivot_longer(
  data = learning.curves[c('trial','lambda1','lambda2','alpha1','alpha2','v1','v2')],
  cols = c('v1','v2'),
  names_to = 'v'
)
learning.curves.v$v = factor(learning.curves.v$v)
learning.curves.v$v = recode(learning.curves.v$v, 'v1'='NT', 'v2'='T')


#Define plot specific parameters
p.ymin = 0
p.ymax = 20
p.yint = 5
p.breaks = seq(p.ymin,p.ymax,p.yint)

p.learning.curves = ggplot(
  data = learning.curves.v,
  aes(x = trial, y = value, group = v, fill=v)
)

p.learning.curves + 
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    stroke = p.point.stroke,
    shape = 21
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_continuous(breaks=1:trials, expand = c(0,.5)) +

  ggtitle("Stimulus\nStrength") + ylab("% Freezing") + xlab("Day") +
  
  p.basetheme +
  theme(
     plot.margin = p.margin3,
     axis.text.x = element_text(angle=0),
     legend.direction = 'horizontal',
     legend.position = c(.5,.95)
  ) 


if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TheoreticalSensitivity.tiff", sep = '_'))}


```

# Stats
## Trauma Stats
```{r}

#comparison of trauma animals' freezing
trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = .(Trauma),
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```


## Trauma Recall
```{r}

#comparison of time in dark side
traumatest.anova = ezANOVA(
  data = traumatest,
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.anova


```


## Weak Shock

### % Shock reactivity
```{r}

wshock.shockreact.anova = ezANOVA(
  data = wshock.startle[wshock.startle$component!='shock_post',],
  dv = motion,
  wid = Animal,
  within = component,
  between = Trauma,
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)
wshock.shockreact.anova

```

### % Freezing
```{r}

wshock.prepost$day = as.character(wshock.prepost$day)
wshock.omni.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$component=='bl'
                        & wshock.prepost$day>=1,],
  dv = freezing,
  wid = Animal,
  within = day,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock.omni.anova


wshock1.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==1 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock1.anova

wshock2.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==2 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock2.anova

wshock3.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==3 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock3.anova

wshock4.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==4 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock4.anova

wshock5.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==5 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock5.anova

wshock6.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==6 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock6.anova

wshock7.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$day==7 & wshock.prepost$component=='bl',],
  dv = freezing,
  wid = Animal,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock7.anova

```


### % Asymptote
```{r}

wshock.prepost$day = as.character(wshock.prepost$day)
wshock.asym.omni.anova = ezANOVA(
  data = wshock.prepost[wshock.prepost$component=='bl',],
  dv = pctasym,
  wid = Animal,
  within = day,
  between = .(Trauma),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
wshock.asym.omni.anova


```