---
title: "SEFL10k5_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


#Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(dplyr)
library(purrr)
```



# Import Data 
Load  files and factorize as necessary
```{r}


#set figure file prefix
f_pfx = 'SEFL10K5'

#load  files
data_vf = read.csv('SEFL10K5_vfdata.csv',header=TRUE)
groups = read.csv('SEFL10K5_groups.csv',header=TRUE)

#factorize as necessary
groups$Animal = factor(groups$Animal)
groups$Group = factor(groups$Group, levels=c('vHC - PSAM', 'BLA - PSAM'))
data_vf$Animal = factor(data_vf$Animal)

# #add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")

```



# Drop subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]

```



# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]

#trauma recall data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$component=='avg',]
traumatest$Drug = traumatest$Recall1
traumatest$Drug[traumatest$subphase==2] = traumatest$Recall2[traumatest$subphase==2]
traumatest$Drug = factor(traumatest$Drug, levels=c("veh","uPSEM"))

#nov stressor data
##prepost startle stimulus
novstressor.prepost = data_vf[data_vf$phase=='novstressor' & data_vf$subphase=='prepost',]
novstressor.prepost$component = factor(novstressor.prepost$component, levels=c('bl','post'))

##startle response
novstressor.startle = data_vf[data_vf$phase=='novstressor' & data_vf$subphase=='startle',]
novstressor.startle$component = factor(
  novstressor.startle$component,
  levels=c('startle_pre','startle_startle','startle_post'))

#novel stressor (sefl) test data
sefltest = data_vf[data_vf$phase=='sefltest' & data_vf$subphase=='avg',]

```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma data
#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component,Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#novel stressor
#novel stressor pre/post
novstressor.prepost.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.prepost,
    component,NS,Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)
#novel stressor startle
novstressor.startle.stats = summarise_at(
  .tbl = group_by(
    .data = novstressor.startle,
    component,NS,Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


#sefl test
sefltest.stats = summarise_at(
  .tbl = group_by(
    .data = sefltest,
    NS_Group),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion')
)


```



#Plots
##Set Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10k5'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =10
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot colors
p.scale.colour = c("red4","#26466D",'paleturquoise4')
p.scale.fill = c("red4","#26466D",'paleturquoise4')
#p.scale.fill = c("white","darkgray","royalblue4","red2",'darkgreen')

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75

#Widths
p.width.bar = .8
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .3

#p.margin
p.margin1 = unit(c(2, 3, .8, 3), "cm")
p.margin2 = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.45, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white", size=.75),
    strip.text = element_text(size=p.textsize.title-2, face="bold"),
    strip.background = element_rect(color=NA, fill=NA),
    axis.line = element_line(color="black", size = p.line.axis.size),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.title.x = element_blank(),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


##Make Plots
####Trauma
#####Trauma Freezing
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Group,
      shape=Group,
      group=interaction(subphase,Group)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.7,.15),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



####Trauma Recall
#####Trauma Recall
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TraumaTest = ggplot(
  data = traumatest.stats,
  aes(x=Drug,
      y=freezing_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.TraumaTest  +
  
  geom_errorbar(
      stat="identity",
      size=p.line.error.size,
      colour = "black",
      aes(ymin = freezing_mean - freezing_sem,
          ymax = freezing_mean + freezing_sem),
      show.legend = FALSE) +
  
    geom_line(
      stat="identity",
      size = p.line.data.size,
    ) +
      
    geom_point(
      stat = "identity",
      size = p.point.size,
      shape = p.point.shape,
      stroke = p.point.stroke,
      show.legend = FALSE
    ) +
  
    geom_line(
      data = traumatest,
      aes(
        x = Drug,
        y = freezing,
        group = Animal
      ),
      alpha=.25,
      size = .5
    ) + 
    
    facet_grid(cols = vars(Region)) +
    
    scale_fill_manual(values=p.scale.fill) +
    scale_colour_manual(values=p.scale.colour) +
    coord_cartesian(ylim=c(p.ymin,p.ymax)) +
    scale_y_continuous(breaks=p.breaks, labels = p.breaks, expand = c(0, 0)) +
    
    labs(y = "% Freezing") +
    p.basetheme 
  
if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecall.tiff", sep = '_'))}


```



# Stats
## trauma
```{r}

trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Group,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```



## traumatest
```{r}

traumatest.anova = ezANOVA(
  data = traumatest,
  wid = Animal,
  dv = freezing,
  between = Region,
  within = Drug,
  type = 3,
  white.adjust = TRUE,
  detailed = TRUE
)

traumatest.anova


```

## sefltest
```{r}

sefltest.anova = ezANOVA(
  data = sefltest,
  wid = Animal,
  dv = freezing,
  between = NS_Group,
  type = 3,
  white.adjust = FALSE,
  detailed = TRUE
)
sefltest.anova

```




