---
title: "SEFL10K6c_Analysis"
author: "Zach"
output:
  html_document: 
    fig_height: 4.5
    fig_width: 4.5
    highlight: kate
    number_sections: yes
    theme: journal
    toc: yes
    toc_depth: 6
editor_options: 
  chunk_output_type: console
---


# Set Global Options
```{r global_options}
knitr::opts_chunk$set(fig.width=4.5, fig.height=4.5, echo=TRUE, warning=FALSE,message=FALSE)
```



# Load Packages 
```{r}
library(ggplot2)
library(ez)
library(knitr)
library(tidyr)
library(lmtest)
library(car)
library(dplyr)
library(purrr)
```



# Import Data 
```{r}

#load  files
data_vf = read.csv('SEFL10K6c_vfdata.csv',header=TRUE)
groups = read.csv('SEFL10K6c_groups.csv',header=TRUE)


#factorize as necessary
groups$Animal = factor(groups$Animal)
data_vf$Animal = factor(data_vf$Animal)
groups$Trec2 = factor(groups$Trec2, levels=c('veh','cno'))
groups$Trec3 = factor(groups$Trec3, levels=c('veh','cno'))


#get dataframe for drug order
drug_order = pivot_longer(
  data = groups[,c('Animal','Trec1','Trec2','Trec3')],
  cols = c('Trec1','Trec2','Trec3'),
  names_to = c('TestName'),
  values_to = 'Drug'
)
drug_order$testnum = gsub("\\D", "", drug_order$TestName)


#add group info to data files
data_vf = inner_join(x=groups,y=data_vf,by="Animal")


#add drug order 
data_vf = left_join(x=data_vf, y=drug_order, by=c('Animal'='Animal','subphase'='testnum'))

```



# Drop subjects
See `groups` dataframe for exclusion rationale.
```{r}

data_vf = data_vf[data_vf$Exclude!=1,]

```


# Subset data
Separate phases (trauma, trauma recall, etc) are placed in unique dataframes for ease of analysis.
```{r}

#trauma data
trauma.freezing = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="shock",]


#trauma shock reactivity
trauma.shockreact = summarise_at(
  .tbl = group_by(
    .data = data_vf[data_vf$phase=='trauma' & data_vf$subphase!="postshock",],
    Animal, subphase, Region),
  .funs = list(motion=mean),
  .vars = c('motion')
)


#trauma test data
traumatest = data_vf[data_vf$phase=='traumatest' & data_vf$component=='avg',]
traumatest$subphase = as.character(traumatest$subphase)
#add bl covariate
traumatest = right_join(
  traumatest,
  traumatest[traumatest$subphase==1, c('Animal','freezing')],
  by = 'Animal',
  suffix = c('','_bl')
)
traumatest$freezing_res = lm(freezing~freezing_bl,traumatest)$residuals


```



# Get summary statistics for plotting
Calculate relevant means and std. errors.
```{r}

#trauma session freezing
trauma.freezing.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.freezing,
    component, Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion','freezing')
)
trauma.freezing.stats$subphase = 'postshock'
trauma.freezing.stats$subphase[trauma.freezing.stats$component=='baseline'] = 'baseline'

#trauma shock reactivity
trauma.shockreact.stats = summarise_at(
  .tbl = group_by(
    .data = trauma.shockreact,
    subphase, Region),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('motion')
)


#trauma test
traumatest.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Region, Drug),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion','freezing_res')
)


traumatest.byorder.stats = summarise_at(
  .tbl = group_by(
    .data = traumatest,
    Region, Trec2, subphase),
  .funs = list(mean=~mean(.), sem=~sd(.)/sqrt(n())),
  .vars = c('freezing','motion','freezing_res')
)


```



# Plots
## Global Plot Parameters
```{r}

#set figure file prefix
f_pfx = '10k6c'

#ggsave
p.save = TRUE

#Plot dimensions
p.dim.width = 4.5 #Plot width (in)
p.dim.height = 4.5 #Plot height (in)
p.dim.dpi = 500 #Plot dpi

#Plot text
p.textsize.title = 20
p.textsize.legend =12
p.textsize.axis.title = 13
p.textsize.axis.text = 12

#Plot line dimensions
p.line.data.size = 1
p.line.axis.size = .5
p.line.bar.size = .7
p.line.error.size = .75
p.line.ind.size = .6
p.line.ind.alpha = .2

#Widths
p.width.bar = .7
p.width.jitter = .3
p.width.error = .5

#Point/dot sizes
p.point.shape = 21
p.point.size = 4
p.point.stroke = 1
p.dot.size = 2.5
p.dot.shape = 21
p.dot.alpha = .25

#Plot colors
p.scale.colour = c("red3", "royalblue3")
p.scale.fill = c("red3", "royalblue3")
#p.margin
p.margin1 = unit(c(1.2, 2.75, 2.5, 2.75), "cm")
p.margin2 = unit(c(2, 3.6, 2.2, 3.6), "cm")
p.margin3 = unit(c(2, 3.25, 2.5, 3.25), "cm") #for trauma

#base theme
p.basetheme = theme_bw() + theme(
    panel.grid = element_blank(), 
    panel.border = element_rect(colour = "white"),
    axis.line = element_line(color="black", linewidth = p.line.axis.size),
    plot.title = element_text(
      size=p.textsize.title, 
      hjust=.5, margin=margin(b=15,t=10), 
      face="bold"),
    axis.title = element_text(size=p.textsize.axis.title, face="bold"),
    axis.text= element_text(size=p.textsize.axis.text,colour="black"),
    axis.text.x= element_text(
      size=p.textsize.axis.title,
      face='bold',
      angle = -90,
      hjust = 0,
      vjust=.5,
      margin=margin(b=10,t=5)),
    legend.position = c(.3,.85),
    legend.title = element_blank(),
    legend.text = element_text(size=p.textsize.legend, face="bold"),
    legend.key = element_rect(colour=NA,fill=NA),
    legend.background = element_rect(fill=NA),
    plot.background = element_rect(fill = "transparent",colour = NA),
    plot.margin = p.margin1
  ) 

#predefine partial function for saving plots
saveplot = partial(
  ggsave,
  width = p.dim.width,
  height = p.dim.height,
  units = "in",
  dpi = p.dim.dpi,
  bg = 'transparent'
)

```


## Make Plots
### Trauma
#### Freezing
```{r, fig.width=4.5, fig.height=4.5}


#Create base layer from group level data
P.Trauma.Freezing = ggplot(
  data = trauma.freezing.stats,
  aes(x=component,
      y=freezing_mean,
      fill=Region,
      shape=Region,
      group=interaction(subphase,Region)))

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 25
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Freezing  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(labels=c('bl','1','2','3','4','5','6','7','8','9','10')) +
  
  labs(
    #title = "Trauma",
    x = "Shock",
    y = "% Freezing"
  ) +
  
  p.basetheme +
  theme(
    plot.title = element_text(margin=margin(b=25,t=5)),
    axis.title.x = element_text(margin=margin(t=-3)),
    axis.text.x= element_text(
      size=p.textsize.axis.title-2,
      face='plain',
      angle = 0,
      vjust=.5),
    legend.position = c(.9,.2),
    plot.margin = p.margin3
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma.tiff", sep = '_'))}

```



#### Shock Reactivity
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.Trauma.Shock = ggplot(
  data = trauma.shockreact.stats,
  aes(x=subphase,
      y=mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 1600
p.yint = 400
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot
P.Trauma.Shock  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = mean - sem,
        ymax = mean + sem,
        width = p.width.error)) +
  
  geom_line(
    stat="identity",
    size = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  scale_fill_manual(values=p.scale.colour) +
  
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  
  labs(
    #title = "Trauma\nShock Reactivity",
    x = "",
    y = "Motion (au)"
  ) +
  
  p.basetheme +
  theme(
    axis.text.x= element_text(
      angle = 0,
      vjust=.5
    ),
    legend.position = c(.4,.85)
  )

#if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "Trauma_ShockReact.tiff", sep = '_'))}


```


### Trauma Recall with Drug
```{r, fig.width=4.5, fig.height=4.5}

#Create base layer from group level data
P.TR_drug = ggplot(
  data = traumatest.byorder.stats[traumatest.byorder.stats$subphase!='3',],
  aes(x=subphase,
      y=freezing_mean,
      fill=Region,
      group=Region)) 

#Define plot specific parameters
p.ymin = 0
p.ymax = 100
p.yint = 20
p.breaks = seq(p.ymin,p.ymax,p.yint)

#Create plot 
P.TR_drug  +
  
  geom_errorbar(
    stat="identity",
    size=p.line.error.size,
    colour = "black",
    aes(ymin = freezing_mean - freezing_sem,
        ymax = freezing_mean + freezing_sem,
        width = p.width.error
        )) +
  
  geom_line(
    stat="identity",
    linewidth = p.line.data.size
  ) +
  
  geom_point(
    stat = "identity",
    size = p.point.size,
    shape = p.point.shape,
    stroke = p.point.stroke
  ) +
  
  facet_grid(cols = vars(Trec2)) +
  
  scale_fill_manual(values=p.scale.fill) +
  scale_colour_manual(values=p.scale.colour) +
  coord_cartesian(ylim=c(p.ymin,p.ymax)) +
  scale_y_continuous(breaks=p.breaks, expand = c(0, 0)) +
  scale_x_discrete(breaks=c(1,2), labels=c('BL','Test')) +
  
  labs(
    y = "% Freezing",
    x = "Test",
    ) +
  
  p.basetheme +
  theme(
    axis.text.x = element_text(angle=0, hjust=.5),
    axis.title.x = element_blank(),
    strip.placement = 'inside',
    strip.text = element_text(size=p.textsize.title, face="bold", hjust=.5),
    strip.background = element_rect(color=NA, fill=NA),
    legend.position = c(1.2,.5),
  )

if (p.save == TRUE) {saveplot(filename = paste(f_pfx, "TraumaRecallDrug.tiff", sep = '_'))}

```




# Stats
## HM4D effects

## trauma
```{r}

trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Region,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```


### Trauma Test Stats
```{r}


traumatest$subphase = as.character(traumatest$subphase)

#first, test if groups differ in their baseline freezing in test 1
traumatest.bl.anova = ezANOVA(
  data = traumatest[traumatest$subphase=='1',],
  dv = freezing,
  wid = Animal,
  between = .(Region, Trec2),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.bl.anova

#second, test if groups differ in their freezing freezing in test 2
traumatest.2.anova = ezANOVA(
  data = traumatest[traumatest$subphase=='2',],
  dv = freezing,
  wid = Animal,
  between = .(Region, Trec2),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.2.anova

#now, test drug effect in test 2, relative to test 1
traumatest.drug.anova = ezANOVA(
  data = traumatest[traumatest$subphase!='3',],
  dv = freezing,
  wid = Animal,
  within = .(subphase),
  between = .(Region, Trec2),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.drug.anova

#test veh effect in test 2, relative to test 1
traumatest.veh.anova = ezANOVA(
  data = traumatest[traumatest$subphase!='3' & traumatest$Trec2=='veh',],
  dv = freezing,
  wid = Animal,
  within = .(subphase),
  between = .(Region),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.veh.anova

#test cno effect in test 2, relative to test 1
traumatest.cno.anova = ezANOVA(
  data = traumatest[traumatest$subphase!='3' & traumatest$Trec2=='cno',],
  dv = freezing,
  wid = Animal,
  within = .(subphase),
  between = .(Region),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.cno.anova



```



### Trauma Stats
```{r}
#comparison of trauma animals' freezing
trauma.fz.anova = ezANOVA(
  data = trauma.freezing,
  dv = freezing,
  wid = Animal,
  within = component,
  white.adjust = TRUE,
  between = Group,
  type = 3,
  detailed = TRUE
)
trauma.fz.anova

```


```{r}


traumatest.ancova = ezANOVA(
  data = traumatest[traumatest$subphase=='2',],
  dv = freezing,
  wid = Animal,
  between = .(Region, Trec2),
  between_covariates = .(freezing_bl),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.ancova


traumatest.ancova2 = ezANOVA(
  data = traumatest[traumatest$subphase!='1',],
  dv = freezing_res,
  wid = Animal,
  between = .(Region),
  within = .(Drug),
  #between_covariates = .(freezing_bl),
  white.adjust = TRUE,
  type = 3,
  detailed = TRUE
)
traumatest.ancova2


```

